---
title: "CITIES evaluation"
subtitle: Structural equation model of CITIES indicators
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '5'
    toc_float: yes
---

### Prep

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=8, warning=FALSE, message=FALSE, cache=TRUE, error=T)
```

```{r}
library(knitr)
library(tidyverse)
library(sjmisc)
library(corrplot)
library(psych)
library(lavaan)
library(semPlot)

setwd("C:/Egnyte/Private/dkillian/Jordan/Population survey/data")

dat <- read_csv("CITIES indicators.csv")

dat <- dat %>%
  select(42:60)

names(dat)

```

### Model 1

The CITIES evaluation posited a set of hypotheses in which municipal institutional capacity building and public outreach leads to a series of outcomes of improved services and operations leading to improved public perception of government responsiveness, effectiveness, confidence in government, and overall stability. 

These outcomes are considered to be both temporally and programmatically ordered. For example, government responsiveness is hypothesized to follow from government effort, while effectiveness is hypothesized to follow from a combination of public outreach as well as improved service delivery. 

Similarly, constructs such as confidence and stability are considered to be higher order. For example, confidence follows from both effectiveness and responsiveness, while stability is an overall legitimacy measure that follows from effectiveness and confidence. 

The following analysis tests these relations in household survey data to assess whether the hypothesized relations fit the empirical patterns in the data. 

```{r}

mod1 <- "
confidence =~ completeObs.confidence_local + completeObs.confidence_muni + completeObs.confidence_gov
effectiveness =~ completeObs.effective_local + completeObs.effective_muni + completeObs.effective_gov
responsiveness =~ completeObs.responsive_local + completeObs.responsive_muni + completeObs.responsive_gov
services =~ completeObs.Water + completeObs.Sanitation + completeObs.Health + completeObs.Transportation + completeObs.Schools + completeObs.Lighting + completeObs.Electricity + completeObs.Roads + completeObs.Parks + completeObs.Trash
stability =~ confidence + effectiveness + responsiveness + services
"

mod1.fit <- cfa(model=mod1, data=dat)

summary(mod1.fit, standardized=T)

```


```{r}

semPaths(mod1.fit,
         whatLabels="std",
         edge.label.cex=1,
         layout="tree",
         rotation=2,
         color="lightblue",
         edge.color="darkgoldenrod",
         style="lisrel")

```


```{r}
fitmeasures(mod1.fit, c("cfi", "tli", "gfi", "rmsea"))
```

The fit indices are good

The root mean square error does not hit desired benchmark of .05, but model should still be workable

Let's see if we can improve the model


```{r}
mod1_mod <- data.frame(modificationindices(mod1.fit, sort=T)) 
kable(mod1_mod)
```

### Model 2

```{r}

mod2 <- "
confidence =~ completeObs.confidence_local + completeObs.confidence_muni + completeObs.confidence_gov
effectiveness =~ completeObs.effective_local + completeObs.effective_muni + completeObs.effective_gov
responsiveness =~ completeObs.responsive_local + completeObs.responsive_muni + completeObs.responsive_gov
services =~ completeObs.Water + completeObs.Sanitation + completeObs.Health + completeObs.Transportation + completeObs.Schools + completeObs.Lighting + completeObs.Electricity + completeObs.Roads + completeObs.Parks + completeObs.Trash
stability =~ confidence + effectiveness + responsiveness + services

completeObs.confidence_gov ~~    completeObs.effective_gov
completeObs.confidence_muni ~~   completeObs.effective_muni
completeObs.confidence_local ~~  completeObs.effective_local
completeObs.effective_gov ~~   completeObs.responsive_gov
completeObs.confidence_gov ~~   completeObs.responsive_gov
completeObs.effective_muni ~~  completeObs.responsive_muni

"

mod2.fit <- cfa(model=mod2, data=dat)

summary(mod2.fit, standardized=T)

```


```{r}
fitmeasures(mod2.fit, c("cfi", "tli", "gfi", "rmsea"))
```

After adding in the top six suggested cross-loadings, the root mean square error meets our desired benchmark of .05 or less

```{r}

semPaths(mod2.fit,
         whatLabels="std",
         edge.label.cex=1,
         layout="tree",
         rotation=2,
         color="lightblue",
         edge.color="darkgoldenrod",
         style="lisrel")

```

### Conclusion

The hypothesized relations are mostly validated in the data. There is one exception, in that responsiveness is inversely related to effectiveness, confidence, and stability. This suggests that for higher order constructs, only improved services and government operations matter. Responsiveness is a genuine outcome at the lower level, but citizens will not perceive greater overall legitimacy without tangible gains in services. 
















