---
title: "Food insecurity explore"
author: "Dan Killian"
date: "10/26/2021"
output: 
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    fig.caption: true
    code_folding: hide
    df_print: kable
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
# standard figure size and generate clean output
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)

source(here("code/00 South Sudan resilience - prep.R"))

dat <- read_dta(here("data/local/SSD resilience baseline prepared.dta")) %>%
  mutate(id=1:3563)

# frq_disag <- function(object, disaggregate, item, label, media) {
#   temp <- object %>%
#     group_by({{disaggregate}}) %>%
#     summarize(Percent=mean({{item}}, na.rm=T),
#               se=std.error({{item}}, na.rm=T)) %>%
#     mutate(var_name={{label}},
#            Media={{media}},
#            lower=Percent-1.96*se,
#            upper=Percent+1.96*se)
#   temp
# }

svy_disag <- function(design, disaggregate, item, label) {
  temp <- design %>%
    group_by({{disaggregate}}) %>%
    summarize(Value=survey_mean({{item}}, na.rm=T)) %>%
    mutate(item={{item}},
           label={{label}},
           lower=Value-1.96*se,
           upper=Value+1.96*se)
  temp
}


# svyrdat <- dat %>%
#   as_survey_design(ids = ea,
#                    strata=county,
#                    weights=final_wt1)
```

# Introduction

The South Sudan Monitoring and Evaluation Support Project (MESP) is conducting a household resilience survey in 13 counties. The purpose of this household survey is to obtain baseline data in the target areas for the indicators included in the Mission's Performance Management Plan (PMP) and the Community Roadmap, in support of USAID/South Sudan's Strategic Framework (2020-2024).

MESP has completed data collection in six counties, and as of October 2021 is carrying out data collection in the remaining seven counties. The study team is currently reviewing the data from six counties in advance of analysis of the full set of 13 counties. This document is one of a series of documents to review various measures and indices relating to resilience.

# Food insecurity

Food insecurity is the lack of confidence that the household will consistently maintain the caloric and dietary needs of its members. The South Sudan resilience baseline asks questions about food insecurity across two different temporal windows: 12 months and four weeks. The following survey items address the issue of food insecurity.

```{r}

fies <- dat %>%
  select(q_422:q_429)

svy_disag <- function(design, disaggregate, item, varname, label) {
  temp <- design %>%
    group_by({{disaggregate}}) %>%
    summarize(Value=survey_mean({{item}}, na.rm=T)) %>%
    mutate(#item={{item}},
           var_name={{varname}},
           label={{label}},
           lower=Value-1.96*Value_se,
           upper=Value+1.96*Value_se)
  temp
}

q422 <- svy_disag(svyrdat, "", q_422, "worried", "Worried about not enough to eat") %>%
  select(4,5,2,6,7)

#q422

q423 <- svy_disag(svyrdat, "", q_423, "unhealthy", "Unable to eat healthy") %>%
  select(4,5,2,6,7)

#q423

q424 <- svy_disag(svyrdat, "", q_424, "few_foods", "Ate few kinds of foods") %>%
  select(4,5,2,6,7)

#q424

q425 <- svy_disag(svyrdat, "", q_425, "skip", "Skipped a meal") %>%
  select(4,5,2,6,7)

#q425

q426 <- svy_disag(svyrdat, "", q_426, "ate_less", "Ate less than needed") %>%
  select(4,5,2,6,7)

#q426

q427 <- svy_disag(svyrdat, "", q_427, "no_food", "Did not have food") %>%
  select(4,5,2,6,7)

#q427

q428 <- svy_disag(svyrdat, "", q_428, "not_eat", "Did not eat") %>%
  select(4,5,2,6,7)

#q428

q429 <- svy_disag(svyrdat, "", q_429, "wholeday", "Went a day without eating") %>%
  select(4,5,2,6,7)

#q429

fies_items <- do.call(rbind, 
                      list(q422,
                           q423,
                           q424,
                           q425,
                           q426,
                           q427,
                           q428,
                           q429))


fies_items

#fies_key <- data.frame(insecure_code=1:8,
#                       insecure_item=fies_items$var_name,
#                       insecure_lab=fies_items$label)

#fies_key

#write_csv(fies_key, here("output/tables/keys/fies key.csv"))

# 
write.csv(fies_items, here("output/tables/food insecurity/fies items.csv"))
# 
fies_items_gt <- fies_items %>%
  gt() %>%
  fmt_percent(3:5,
              decimals=1)

gtsave(fies_items_gt, here("output/tables/food insecurity/fies items.rtf"))

```

```{r echo=F, fig.cap="Items comprising Food Insecurity Experience Scale (FIES)"}
fies_items_gt

```

```{r}
svyrdat %>%
  group_by(fies_cat) %>%
  summarize(survey_mean())
```

We can create an index value that is simply the sum of items the respondent agrees to. This has already been calculated under the variable 'fies_raw'.

```{r}
ggplot(dat, aes(fies_raw, weight=final_wt1)) + 
  geom_bar()

```

A great majority of respondents agreed with all eight items, raising questions about the suitability of this data for scale construction. The weighted mean scale value is 7.7. Here is the mean scale value across county.

```{r}

fies_mn <- svyrdat %>%
  group_by() %>%
  summarize(fies=survey_mean(fies_raw, na.rm=T)) %>%
  mutate(lower=fies - 1.96*fies_se,
         upper=fies + 1.96*fies_se,
         measure="")

  select(1) %>%
  unlist()

fies_mn # 7.58

```

```{r}
ggplot(fies_mn, aes(fies, measure)) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, color=medium_blue) +
  #geom_hline(yintercept=1, color=light_blue, size=1) +
  geom_segment(aes(x=0, xend=8, y=1, yend=1), color=light_blue) + 
  geom_label(aes(label=round(fies,1)), color=medium_blue, size=8) +
  scale_x_continuous(limits=c(0,8),
                     breaks=0:8) +
  labs(x="",
       y="") +
  geom_ribbon(aes(xmin=1, xmax=3))

ggsave(here("output/viz/food security/fies overall weighted.png"),
       device="png",
       type="cairo",
       height=1.2,
       width=4)

```

```{r}
fies_county <- svyrdat %>%
  group_by(county) %>%
  summarize(fies=survey_mean(fies_raw, na.rm=T)) %>%
  mutate(lower=fies-1.96*fies_se,
         upper=fies+1.96*fies_se) %>%
  select(1,2,4,5)

#fies_county

a <- ggplot(fies_county, aes(fies, county)) + 
  geom_vline(aes(xintercept=fies_mn), color="darkgoldenrod2", size=1, alpha=.8) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), color=medium_blue, width=0) + 
  geom_label(aes(label=round(fies,2)), color=medium_blue, size=3) + 
  scale_x_continuous(limits=c(6,8),
                     breaks=5:8) + 
  labs(x="",
       y="")
```

```{r echo=F, fig.cap="Food insecurity experience scale (FIES), by county"}
a
```

```{r}
# f2 <- dat %>%
#   select(q_430:q_435)

# head(f2)
# map(f2, frq)
```

Let's look at how well this data can be fit into an item response theory framework.

# Analytical models

## FAO models

```{r}
library(ltm)
library(eRm)
library(RM.weights)

names(dat)
names(fies_items)

rash <- fies_items %>%
  select(1:8)

rash <- dat %>%
  select(q_422:q_429) %>%
#  as.data.frame() %>%
  map(., as.numeric) %>%
  as.data.frame() %>%
  na.omit()

rash <- map(rash, as.numeric) %>%
  as.matrix()

str(rash)

rash2 <- dat %>%
  select(q_422:q_429, hh_wt)

head(rash)

r1 <- RM.w(rash)
str(rash)

r1
summary(r1)

```

```{r}
r1$b
```

# LTM package

```{r}
library(ltm)

descript(fies)

```

```{r}
plot(descript(fies))
```

## ltm

```{r}

l1 <- ltm(fies ~ z1)
l1
summary(l1)
```

```{r}
plot(l1, type="ICC")
```

```{r}
plot(l1, type="IIC")
```

```{r}
plot(l1_scores, type="loadings")
```

```{r}
plot(l1, 
     type="IIC", 
     items=0)
```

```{r}
person.fit(l1)
```

```{r}

l1_scores <- factor.scores(l1)


l1_scores_dat <- l1_scores$score.dat

sum(l1_scores_dat$Obs)

ggplot(l1_scores_dat, aes(z1, weight=Obs)) + 
  geom_density() +
  scale_x_continuous(limits=c(-2.5,.5))

```

```{r}
plot(l1_scores)
```

```{r}

```

```{r}
describe(dat$fies)



```

## rasch

```{r}
r1 <- rasch(fies)
summary(r1)
```

```{r}
coef(r1)
```

```{r}
plot(r1, 
     type="ICC",
     legend=T)
```

```{r}
plot(r1, 
     type="IIC",
     legend=T)
```

```{r}
plot(r1, 
     type="IIC",
     items=0) 
```

```{r}
r1_scores <- factor.scores(r1, method="EAP")$score.dat
head(r1_scores)

```

```{r}
fies_index <- fies %>%
  mutate(id=1:3563) %>%
  merge(r1_scores) %>%
  rename(fies_index=z1)

head(fies_index)

describe(fies_index$fies_index)

ggplot(fies_index, aes(fies_index)) + 
  geom_density() + 
  scale_x_continuous(limits=c(-2,.75))

```

```{r}
r1_pfit <- person.fit(r1)
summary(r1_pfit)
```

## TAM package

```{r}
library(TAM)
library(WrightMap)
citation("WrightMap")
```

```{r}
t1 <- tam(fies)
```

```{r}
summary(t1)
```

```{r}
t1_itemfit <- tam.fit(t1)

summary(t1_itemfit)

```

```{r}
IRT.WrightMap(t1)
```

Not good results. No variation in item difficulty.

```{r}
t1_scores <- tam.wle(t1) %>%
  as.data.frame() %>%
  mutate(theta_2 = theta+10)

head(t1_scores)
```

```{r}
raw_test <- dat %>%
  select(id, fies_raw)
```

```{r}
ggplot(t1_scores, aes(theta)) + 
  geom_density() + 
  scale_x_continuous(limits=c(-8,0))
```

```{r}
out <- t1_scores %>%
  group_by(PersonScores) %>%
  summarize(theta=mean(theta, na.rm=T),
            error=mean(error, na.rm=T)) %>%
  mutate(theta_2 = theta + 10)

out
```

```{r}
t1_persfit <- tam.personfit(t1)
summary(t1_persfit)

```

```{r}
dat <- dat %>%
  mutate(fies_index_tam = t1_scores$theta_2)

describe(dat$fies_raw)
describe(dat$fies_index_tam)

```

```{r}

```

```{r}

```

# Dietary diversity

```{r}

# frq(dat$fies_raw)

diet <- dat %>%
select(q_403:q_419)

map(diet, frq)

```

## Diet descriptives

Rank foods eaten

```{r}
foods_temp <- svyrdat %>%
  summarize(cereals = survey_mean(q_403, na.rm=T),
            roots = survey_mean(q_404, na.rm=T),
            vitAveg = survey_mean(q_405, na.rm=T),
            leafygreens = survey_mean(q_406, na.rm=T),
            otherveg = survey_mean(q_407, na.rm=T),
            vitAfruits = survey_mean(q_408, na.rm=T),
            otherfruits = survey_mean(q_409, na.rm=T),
            organmeat = survey_mean(q_410, na.rm=T),
            fleshmeat = survey_mean(q_411, na.rm=T),
            bushmeat = survey_mean(q_412, na.rm=T),
            eggs = survey_mean(q_413, na.rm=T),
            fish = survey_mean(q_414, na.rm=T),
            legumes = survey_mean(q_415, na.rm=T),
            milk = survey_mean(q_416, na.rm=T),
            oils = survey_mean(q_417, na.rm=T),
            sweets = survey_mean(q_418, na.rm=T),
            spices = survey_mean(q_419, na.rm=T))

foods

foods_mn <- foods_temp %>%
  select(!contains("se")) %>%
  melt() %>%
  rename(percent=value)

foods_mn


foods_se <- foods_temp %>%
  select(contains("se")) %>%
  melt() %>%
  rename(se=value)

foods_se

foods <- foods_mn %>%
  cbind(foods_se[,2]) %>%
  rename(se=3) %>%
  mutate(lower=percent-1.96*se,
         upper=percent+1.96*se,
         food_lab=diet_labs) %>%
  select(food=1, 6, everything()) %>%
  arrange(desc(percent))

foods

write_csv(foods, here("output/tables/food insecurity/foods weighted.csv"))

foods_gt <- foods %>%
  select(2:3) %>%
  gt() %>%
  fmt_percent(2,
              decimals=1)

foods_gt  

gtsave(foods_gt,
       here("output/tables/food insecurity/foods weighted.rtf"))

```

```{r}

ggplot(foods, aes(x=percent, y=fct_reorder(food_lab, percent))) + 
  geom_vline(xintercept=c(4,6), size=1, linetype="dashed", color=dark_grey) +
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
#  geom_point(size=3, color=light_blue) +
  geom_label(aes(label=paste(round(percent,3)*100, "%", sep="")), 
             color=medium_blue,
             label.padding=unit(.125, "lines")) +
  labs(x="",
       y="") + 
  scale_x_continuous(limits=c(0,1),
                     breaks=seq(0,1,.2),
                     labels=percent) 


ggsave(here("output/viz/food security/foods eaten weighted.png"),
       device="png",
       type="cairo",
       height=4.5,
       width=6)

```

## Diet IRT

```{r}
ltm_diet <- ltm(diet ~ z1)
ltm_diet

```

```{r}

ltm_diet_out <- coef(ltm_diet) %>%
  as.data.frame() %>%
  mutate(food = diet_labs) %>%
  rownames_to_column("item") %>%
  select(1,4,difficulty=2,discrimination=3)

ltm_diet_out

write_csv(ltm_diet_out, here("output/tables/food insecurity/diet irt.csv"))

ltm_diet_gt <- ltm_diet_out %>%
  gt() %>%
  fmt_number(3:4,
             decimals=2)

ltm_diet_gt

gtsave(ltm_diet_gt, here("output/tables/food insecurity/diet irt.rtf"))

```

## Diet factors 

```{r}
fa.parallel(diet)
```

### 6 factors, 3 components

```{r}

fa_diet_6 <- fa(diet,
                nfactors=6,
                scores="tenBerge",
                fm="ml",
                cor="tet")

fa_diet_6
```

```{r}
fa_diet_6_ldngs <- fa_diet_6$loadings %>%
  unclass() %>%
  as.data.frame() %>%
  rownames_to_column("item") %>%
  mutate(food=diet_labs,
         difficulty=ltm_diet_out$difficulty,
         discrimination=ltm_diet_out$discrimination) %>%
  select(1,8,2:7,9, 10)

fa_diet_6_ldngs

write_csv(fa_diet_6_ldngs, here("output/tables/food insecurity/hdds factor loadings.csv"))

diet6_ldngs <- fa_diet_6_ldngs %>%
  gt() %>%
  fmt_number(3:8, decimals=3) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightblue")
    ),
    locations = cells_body(
      columns = ML3,
      rows = ML3 > .3999
    ))

diet6_ldngs


gtsave(diet6_ldngs, here("output/tables/food insecurity/hhds factor loadings.rtf"))

```

ML3: meat, bush meat, organ meat, eggs, seafood

ML5: Vit A fruits, other fruits, roots/tubers, sweets

ML6: oil/fats, milk products

ML1: Vit A veggies, roots/tubers

ML2: Fish

ML4: spices, cereals, other veggies

```{r}
fa_diet_6_scores <- data.frame(fa_diet_6$scores) %>%
  set_names(nm=c("diet_fac_meats",
                 "diet_fac_vitAfruits",
                 "diet_fac_oilfats",
                 "diet_fac_vitAveggies",
                 "diet_fac_fish",
                 "diet_fac_spicecereals"))

dat <- dat %>%
cbind(fa_diet_6_scores)

ggplot(dat, aes(ML3, hdds)) + 
#geom_point() + 
stat_smooth(se=F, color="dodgerblue2") +
  stat_smooth(aes(y=ML5), se=F, color=light_grey) +
  stat_smooth(aes(y=ML6), se=F, color=light_blue) +
  stat_smooth(aes(y=ML1), se=F, color=usaid_red) +
  stat_smooth(aes(y=ML2), se=F, color=usaid_blue) +
  stat_smooth(aes(y=ML4), se=F, color=dark_grey) +
  scale_x_continuous(limits=c(-1.5,1.7),
                     breaks=seq(-1.5,1.5,.5)) +
  scale_y_continuous(breaks=0:12) + 
  labs(x="Dietary diversity factors",
       y="HDDS") + 
  theme(axis.title.y=element_text(angle=0, vjust=.5)) + 
  annotate("text", x=.8, y=9, label="Meat, eggs, seafood", color="dodgerblue2")

ggsave(here("output/viz/food security/HHDS factors.png"),
       type="cairo",
       device="png",
       height=4,
       width=7)

```

### 5 factors

```{r}

fa_diet_5 <- fa(diet,
                nfactors=5,
                scores="tenBerge",
                fm="ml",
                cor="tet")

fa_diet_5
```

```{r}
fa_diet_5_ldngs <- fa_diet_5$loadings %>%
  unclass() %>%
  as.data.frame() %>%
  rownames_to_column("item") %>%
  mutate(food=diet_labs,
         difficulty=ltm_diet_out$difficulty,
         discrimination=ltm_diet_out$discrimination) 
%>%
  select(1,8,2:7,9, 10)

fa_diet_5_ldngs

write_csv(fa_diet_6_ldngs, here("output/tables/food insecurity/hdds factor loadings.csv"))

diet6_ldngs <- fa_diet_6_ldngs %>%
  gt() %>%
  fmt_number(3:8, decimals=3) %>%
  tab_style(
    style = list(
      cell_fill(color = "lightblue")
    ),
    locations = cells_body(
      columns = ML3,
      rows = ML3 > .3999
    ))

diet6_ldngs


gtsave(diet6_ldngs, here("output/tables/food insecurity/hhds factor loadings.rtf"))

```



```{r}
l1 <- lm(fies_raw ~ MR1 + MR2 + MR3 + MR4 + MR5 + MR6,
data=dat2)

summary(l1)
```

```{r}
inc <- dat %>%
select(q_401_a_bin,
q_401_b_bin,
q_401_c_bin,
q_401_d_bin,
q_401_e_bin,
q_401_f_bin,
q_401_g_bin,
q_401_h_bin,
q_401_i_bin,
q_401_j_bin,
q_401_k_bin,
q_401_j_bin,
q_401_k_bin,
q_401_l_bin,
q_401_m_bin,
q_401_n_bin,
q_401_o_bin,
q_401_p_bin,
q_401_q_bin,
q_401_r_bin,
q_401_s_bin,
q_401_t_bin,
q_401_u_bin)

str(inc)
head(inc)

fa.parallel(inc, cor="tet")

```

```{r}
fa_inc_6 <- fa(inc,
               cor="tet",
               scores="tenBerge",
               fm="ml",
               nfactors=6)

fa_inc_6

```

# Food insecurity one month

```{r}

fies2 <- dat %>%
  select(q_430:q_435)

map(fies2, frq)

```

```{r}
q432 <- svyrdat %>%
  summarize(q432=survey_mean(q_432, na.rm=T))

q432

```

```{r}
q433 <- svyrdat %>%
  group_by(q_433) %>%
  summarize(cat = survey_mean())

q433

```


```{r}

fies2[is.na(fies2)] <- 0

fa.parallel(fies2,
            cor="poly")
```

3 factors, 1 component. But we want a single factor or component

```{r}
fa_fies2 <- fa(fies2, 
               cor="poly",
               #scores="tenBerge")
               fm="ml")

fa_fies2
```

How does this compare to IRT? 


```{r}
irt_fies2 <- grm(fies2, constrained=F) 

irt_fies2
```
q_432 (go to sleep hungry) has highest discrimination. This agrees with the factor weights. 


```{r}
fa_fies2_scrs <- fa_fies2$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(fies2_fac = fa_fies2_scrs$ML1,
         fies2_fac_resc = scales::rescale(fies2_fac, c(0,100)))

describe(dat$fies2_fac_resc)
ggplot(dat, aes(fies2_fac)) + 
  geom_density()
```

```{r}
ggplot(dat, aes(fies2_fac_resc)) + 
  geom_bar()
```



```{r}
fies3 <- dat %>%
  select(q_430,
         q_432,
         q_434)

map(fies3, frq)
```



```{r}
fa.parallel(fies3,
            cor="tet")
```

1 factor, 1 component

```{r}
fa_fies3 <- fa(fies3,
               cor="tet",
               #scores="tenBerge",
               fm="ml")

fa_fies3

```




```{r}
fa_fies3_scrs <- fa_fies3$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(fies3_fac = fa_fies3_scrs$ML1,
         fies3_fac_resc = scales::rescale(fies3_fac, c(0,100)))

describe(dat$fies3_fac_resc)
ggplot(dat, aes(fies3_fac)) + 
  geom_density()
```



```{r}
frq(dat$fies3_fac_resc)
```



```{r}
ggplot(dat, aes(fies3_fac_resc)) + 
  geom_bar()
```



```{r}
fies4 <- dat %>%
  select(q_422:q_435)

fies4[is.na(fies4)] <- 0

names(fies4)
```

```{r}
fa.parallel(fies4,
            cor="poly")
```

4 factors, 2 components

```{r}
fa_fies4 <- fa(fies4,
               cor="poly",
               #scores="tenBerge",
               fm="ML")

fa_fies4

```


```{r}
fa_fies4_scrs <- fa_fies4$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(fies4_fac = fa_fies4_scrs$ML1,
         fies4_fac_resc = scales::rescale(fies4_fac, c(0,100)))

describe(dat$fies4_fac_resc)

```


```{r}
ggplot(dat, aes(fies4_fac)) + 
  geom_density()
```


```{r}
ggplot(dat, aes(fies4_fac_resc)) + 
  geom_bar()

```


```{r}
frq(dat$fies4_fac_resc)
```



```{r}

```


# FIES explore

```{r}

l1 <- svyolr(ordered(fies_raw) ~ inc_fac_livestocksales + inc_fac_pettytrade + inc_fac_agwage + inc_fac_wage + inc_fac_proprent + inc_fac_farmer + inc_fac_safetynet + 
               household_members + urban + as.factor(hh_head_sex) + as.factor(county),
             method="probit",
             design=svydat)
summary(l1)

```


```{r}
m1 <- svyglm(fies_raw ~ absorp_latent,
             design=svydat)

summary(m1)

```


```{r}
m2 <- stan_glmer(fies_raw ~ absorp_latent + (1|ea),
                 parallel=T,
                 cores=4,
                 data=dat)

summary(m2, digits=3)
fixef(m2)
```

## FIES and income groups

```{r}
ggplot(dat, aes(y=fies_raw)) + 
  #stat_smooth(aes(x=inc_fac_livestocksales), color=light_blue, se=F, span=.9) +
  #stat_smooth(aes(x=inc_fac_pettytrade), color=medium_blue, se=F, span=.9) +
  #stat_smooth(aes(x=inc_fac_agwage), color=usaid_blue, se=F, span=.9) +
  #stat_smooth(aes(x=inc_fac_wage), color=light_grey, se=F, span=.9) +
  stat_smooth(aes(x=inc_fac_proprent), color=medium_grey, se=F, span=.9, size=2) +
  #stat_smooth(aes(x=inc_fac_farmer), color=dark_grey, se=F, span=.9) +
  stat_smooth(aes(x=inc_fac_safetynet), color=usaid_red, se=F, span=.9, size=2) + 
  labs(x="Property rental (grey)\nSafety nets (red)",
       y="")

ggsave(here("output/viz/food security/income groups and food security.png"),
            device="png",
            type="cairo",
            height=4,
            width=7)
```
```{r}
l1 <- svyglm(fies_raw ~ inc_fac_livestocksales + inc_fac_pettytrade + inc_fac_agwage + inc_fac_wage + inc_fac_proprent + inc_fac_farmer + inc_fac_safetynet + 
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)

summary(l1)

describe(dat$fac_inc_livestocksales)
```

## Rank of income sources

```{r}
names(inc)

```

```{r}
inc_labs
```


```{r}
inc_temp <- svyrdat %>%
  summarize(farm = survey_mean(q_401_a_bin, na.rm=T),
            cattle = survey_mean(q_401_b_bin, na.rm=T),
            goat = survey_mean(q_401_c_bin, na.rm=T),
            sheep = survey_mean(q_401_d_bin, na.rm=T),
            fish = survey_mean(q_401_e_bin, na.rm=T),
            agwage_in = survey_mean(q_401_f_bin, na.rm=T),
            agwage_out = survey_mean(q_401_g_bin, na.rm=T),
            wage_in = survey_mean(q_401_h_bin, na.rm=T),
            wage_out = survey_mean(q_401_i_bin, na.rm=T),
            salary = survey_mean(q_401_j_bin, na.rm=T),
            bush = survey_mean(q_401_k_bin, na.rm=T),
            honey = survey_mean(q_401_l_bin, na.rm=T),
            petty_other = survey_mean(q_401_m_bin, na.rm=T),
            petty_own = survey_mean(q_401_n_bin, na.rm=T),
            otherself_ag = survey_mean(q_401_o_bin, na.rm=T),
            otherself_nonag = survey_mean(q_401_p_bin, na.rm=T),
            rent = survey_mean(q_401_q_bin, na.rm=T),
            remit = survey_mean(q_401_r_bin, na.rm=T),
            gift = survey_mean(q_401_s_bin, na.rm=T),
            safety = survey_mean(q_401_t_bin, na.rm=T))
            
inc_temp

inc_mn <- inc_temp %>%
  select(!contains("_se")) %>%
  melt() %>%
  rename(percent=value)

inc_mn


inc_se <- inc_temp %>%
  select(contains("_se")) %>%
  melt() %>%
  rename(se=value)

inc_se

incs <- inc_mn %>%
  cbind(inc_se[,2]) %>%
  rename(se=3) %>%
  mutate(lower=percent-1.96*se,
         upper=percent+1.96*se,
         inc_lab=inc_labs) %>%
  select(income=1, 6, everything()) %>%
  arrange(desc(percent))

incs

```

```{r}

ggplot(incs, aes(x=percent, y=fct_reorder(inc_lab, percent))) + 
  geom_vline(xintercept=c(4,6), size=1, linetype="dashed", color=dark_grey) +
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
#  geom_point(size=3, color=light_blue) +
  geom_label(aes(label=paste(round(percent,3)*100, "%", sep="")), 
             color=medium_blue,
             label.padding=unit(.125, "lines")) +
  labs(x="",
       y="") + 
  scale_x_continuous(limits=c(0,1),
                     breaks=seq(0,1,.2),
                     labels=percent) 


ggsave(here("output/viz/income sources ranked.png"),
       device="png",
       type="cairo",
       height=5.5,
       width=7)

```

## Income factors, using ranked sources


