---
title: "Shocks explore"
author: "Dan Killian"
date: "10/28/2021"
output: 
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    fig.caption: true
    code_folding: hide
    df_print: kable
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
# standard figure size and generate clean output
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)

knitr::opts_knit$set(root.dir=here()) # doesn't seem to work

source(here("code/00 South Sudan resilience - prep.R"))

#dat <- read_dta(here("data/local/SSD resilience baseline prepared.dta"))

dat <- read_dta(here("data/local/SSD resilience baseline prepared (9 Nov 2021).dta"))

# frq_disag <- function(object, disaggregate, item, label, media) {
#   temp <- object %>%
#     group_by({{disaggregate}}) %>%
#     summarize(Percent=mean({{item}}, na.rm=T),
#               se=std.error({{item}}, na.rm=T)) %>%
#     mutate(var_name={{label}},
#            Media={{media}},
#            lower=Percent-1.96*se,
#            upper=Percent+1.96*se)
#   temp
# }

svy_disag <- function(design, disaggregate, item, label) {
  temp <- design %>%
    group_by({{disaggregate}}) %>%
    summarize(Value=survey_mean({{item}}, na.rm=T)) %>%
    mutate(item={{item}},
           label={{label}},
           lower=Value-1.96*se,
           upper=Value+1.96*se)
  temp
}


# svyrdat <- dat %>%
#   as_survey_design(ids = ea,
#                    strata=county,
#                    weights=final_wt1)
```


# Introduction

The South Sudan Monitoring and Evaluation Support Project (MESP) is conducting a household resilience survey in 13 counties. The purpose of this household survey is to obtain baseline data in the target areas for the indicators included in the Mission's Performance Management Plan (PMP) and the Community Roadmap, in support of USAID/South Sudan's Strategic Framework (2020-2024).

MESP has completed data collection in six counties, and as of October 2021 is carrying out data collection in the remaining seven counties. The study team is currently reviewing the data from six counties in advance of analysis of the full set of 13 counties. This document is one of a series of documents to review various measures and indices relating to resilience.

# Shocks and stressers

## Overall incidence of shocks

Unweighted

```{r}

# shck_mn <- dat %>%
#   select(shock_flood:shock_death) %>%
#   summarize_all(mean, na.rm=T) %>%
#   t() %>%
#   as.data.frame() %>%
#   rownames_to_column() %>%
#   set_names(nm=c("var_name","freq")) %>%
#   left_join(shock_key) %>%
#   select(1,3,4,2) %>%
#   arrange(desc(freq))
#   
# shck_mn

shck_mn_se <- dat %>%
  select(shock_flood:shock_death) %>%
  summarize(across(everything(),
                   list(mn = ~mean(.,na.rm=T), se = ~std.error(.,na.rm=T)))) %>%
#                   .names="{.col}.{.fn}")) %>% # name the separator from summarize
  pivot_longer(cols=1:32,
               names_to=c("discard", "var_name","measure"),
               names_sep="_",
               values_to="value") %>%
  select(-1) %>%
  pivot_wider(names_from=measure,
              values_from=value) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se,
         shock_lab=shock_labs,
         shock=1:16) %>%
  select(1,7,6, 2:5) %>%
  mutate(overall_rank = rank(-mn)) %>%
  arrange(desc(mn))

#write_csv(shck_mn_se, here("output/tables/shocks/shock incidence overall, unweighted.csv"))
  
shck_mn_se

```
```{r}

ggplot(shck_mn_se, aes(x=mn, y=fct_reorder(shock_lab, mn))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(labels=percent,
                     limits=c(0,1))

```

Weighted

```{r}

shck_svy <- svyrdat %>%
  select(shock_flood:shock_death) %>%
  summarize_all(survey_mean, na.rm=T) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column() %>%
  set_names(nm=c("var_name","freq"))

shck_mn_svy <- shck_svy %>%
  filter(row_number() %% 2 ==1) %>%
  rename(mn=freq) %>%
  mutate(shock_lab=shock_labs)

shck_se_svy <- shck_svy %>%
  filter(row_number() %% 2 == 0) %>%
  rename(se=freq) %>%
  mutate(shock_lab=shock_labs) %>%
  select(-1)

shck_mn_se_svy <- shck_mn_svy %>%
  left_join(shck_se_svy) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se) %>%
  select(1,3,2,4:6)

shck_mn_se_svy

```

```{r}

ggplot(shck_mn_se_svy, aes(x=mn, y=fct_reorder(shock_lab, mn))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(labels=percent,
                     limits=c(0,1))

```

## Incidence of shocks, by state

```{r}
shck_state_mn_se <- dat %>%
  select(state, shock_flood:shock_death) %>%
  group_by(state) %>%
  summarize(across(shock_flood:shock_death,
                   list(mn = ~mean(., na.rm=T), se = ~std.error(., na.rm=T)))) %>%
  pivot_longer(cols=2:33,
               names_to=c("discard", "var_name","measure"),
               names_sep="_",
               values_to="value") %>%
  select(-2) %>%
  pivot_wider(names_from=measure,
              values_from=value) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se) %>%
  cbind(shock_key) %>%
  select(1,2, 7,8,3:6) %>%
  group_by(state) %>%
  mutate(state_rank=rank(-mn)) %>%
  arrange(state,desc(mn)) %>%
  ungroup() 
  
shck_state_mn_se

#write_csv(shck_state_mn_se, here("output/tables/shocks/shock incidence by state, unweighted.csv"))

```

```{r fig.height=7, fig.width=11}

ggplot(shck_state_mn_se, aes(x=mn, y=fct_reorder(shock_lab, mn))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(labels=percent,
                     limits=c(0,1)) +
  facet_wrap(~state) +
  faceted


```

## Incidence of shocks, by county

```{r}

shck_county_mn_se <- dat %>%
  select(state, county, shock_flood:shock_death) %>%
  group_by(state, county) %>%
  summarize(across(shock_flood:shock_death,
                   list(mn = ~mean(., na.rm=T), se = ~std.error(., na.rm=T)))) %>%
  pivot_longer(cols=3:34,
               names_to=c("discard", "var_name","measure"),
               names_sep="_",
               values_to="value") %>%
  select(-3) %>%
  pivot_wider(names_from=measure,
              values_from=value) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se) %>%
  ungroup() %>%
  mutate(shock_lab=rep(shock_labs,13)) %>%
  select(1,2, 3, 8, 4:7) %>%
  group_by(county) %>%
  mutate(county_rank=rank(-mn)) %>%
  arrange(county, desc(mn)) %>%
  ungroup() 
  
#shck_state_mn_se

#write_csv(shck_county_mn_se, here("output/tables/shocks/shock incidence by county, unweighted.csv"))

```

```{r fig.height=10, fig.width=11}

ggplot(shck_county_mn_se, aes(x=mn, y=fct_reorder(shock_lab, mn))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(labels=percent,
                     limits=c(0,1)) +
  facet_wrap(~state + county,
             ncol=5) +
  faceted

```
## Shock clustering

```{r}
shocks <- dat %>%
  select(shock_flood:shock_death)

fa.parallel(shocks,
            cor="tet")
```

```{r}
fa_shocks_5 <- fa(shocks,
                  nfactors=5,
                  cor="tet",
                  scores="tenBerge",
                  fm="ml")

fa_shocks_5
```
ML1: crop shocks

ML3: livestock shocks

ML2: land, erosion, flood

ML5: illness, death

ML4: food prices, illness





## Shock severity

## Overall severity of shocks

Unweighted

```{r}

# shck_mn <- dat %>%
#   select(shock_flood:shock_death) %>%
#   summarize_all(mean, na.rm=T) %>%
#   t() %>%
#   as.data.frame() %>%
#   rownames_to_column() %>%
#   set_names(nm=c("var_name","freq")) %>%
#   left_join(shock_key) %>%
#   select(1,3,4,2) %>%
#   arrange(desc(freq))
#   
# shck_mn

shck_mn_se <- dat %>%
  select(shock_flood:shock_death) %>%
  summarize(across(everything(),
                   list(mn = ~mean(.,na.rm=T), se = ~std.error(.,na.rm=T)))) %>%
#                   .names="{.col}.{.fn}")) %>% # name the separator from summarize
  pivot_longer(cols=1:32,
               names_to=c("discard", "var_name","measure"),
               names_sep="_",
               values_to="value") %>%
  select(-1) %>%
  pivot_wider(names_from=measure,
              values_from=value) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se,
         shock_lab=shock_labs,
         shock=1:16) %>%
  select(1,7,6, 2:5) %>%
  mutate(overall_rank = rank(-mn)) %>%
  arrange(desc(mn))

#write_csv(shck_mn_se, here("output/tables/shocks/shock incidence overall, unweighted.csv"))
  
shck_mn_se

```


```{r}

sev_county <- dat %>%
  select(state, county, shock_flood:shock_death) %>%
  group_by(state, county) %>%
  summarize(across(shock_flood:shock_death,
                   list(mn = ~mean(., na.rm=T), se = ~std.error(., na.rm=T)))) %>%
  pivot_longer(cols=3:34,
               names_to=c("discard", "var_name","measure"),
               names_sep="_",
               values_to="value") %>%
  select(-3) %>%
  pivot_wider(names_from=measure,
              values_from=value) %>%
  mutate(lower=mn-1.96*se,
         upper=mn+1.96*se) %>%
  ungroup() %>%
  mutate(shock_lab=rep(shock_labs,13)) %>%
  select(1,2, 3, 8, 4:7) %>%
  group_by(county) %>%
  mutate(county_rank=rank(-mn)) %>%
  arrange(county, desc(mn)) %>%
  ungroup() 
  
#shck_state_mn_se

#write_csv(shck_county_mn_se, here("output/tables/shocks/shock incidence by county, unweighted.csv"))

```

## Shock exposure


```{r}
ggplot(dat, aes(shock_exposure_index)) + 
  geom_density(color=light_blue)
```

```{r}
ggplot(dat, aes(shock_exposure_index)) + 
  #geom_bar() + 
  geom_density(color=light_blue) +
  facet_wrap(~state) +
  faceted
```

```{r}
ggplot(dat, aes(shock_exposure_index)) + 
  #geom_bar() + 
  geom_density(color=light_blue) +
  facet_wrap(~county) +
  faceted
```


```{r}
expos <- dat %>%
  group_by(state, county) %>%
  summarize(exposure=mean(shock_exposure_index, na.rm=T),
            se=std.error(shock_exposure_index, na.rm=T)) %>%
  mutate(lower=exposure-1.96*se,
         upper=exposure+1.96*se)

expos
```
Unweighted

```{r}
ggplot(expos, aes(x=exposure, y=fct_reorder(county, exposure))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(limits=c(0,144)) 

```

```{r fig.height=10, fig.width=9}
ggplot(expos, aes(x=exposure, y=fct_reorder(county, exposure))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(limits=c(0,144),
                     breaks=seq(0,125,25)) +
  facet_wrap(~state,
             scales="free",
             ncol=2) + 
  faceted

```

Weighted

```{r}
expos_wt <- svyrdat %>%
  group_by(county) %>%
  summarize(exposure=survey_mean(shock_exposure_index, na.rm=T)) %>%
  mutate(lower=exposure-1.96*exposure_se,
         upper=exposure+1.96*exposure_se)

expos_wt
```

```{r}
ggplot(expos_wt, aes(x=exposure, y=fct_reorder(county, exposure))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=light_blue) +
  geom_point(size=3, color=light_blue) +
  labs(x="",
       y="") + 
  scale_x_continuous(limits=c(0,144)) 

```

# Ability to recover

# 
