---
title: "South Sudan resilience baseline"
subtitle: "Survey frequencies"
author: "Dan Killian"
toc: true
toc-depth: 3
number-sections: true
format:
  html:
    code-fold: true
editor: visual
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(autodep=T, fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)
source("00 South Sudan resilience - prep.R")
library(crosstalk) #Allows objects to "talk" to each other
library(reactable) #Creates a table that can be interactive

hh <- read_dta(here("data/local/mesp_household_baseline_hh_survey_schedule_combined_weighted.dta")) %>%
  rename(age = q_304, 
         sex=q_302)

```

# Household roster

The following frequencies describe the 41,824 household members enumerated in the 7,872 household interviews.

## 302 Sex of household member

```{r}
frq(hh$sex) %>%
  data.frame() %>%
  select(3:5) %>%
  gt() 
```

## 303 Relationship to head of household

```{r}
frq(hh$q_303) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 304 Age

```{r}
describe(hh$age)
```

```{r}
ggplot(hh, aes(age)) + 
  geom_density(color="blue", fill="lavender", alpha=.8)
```

## 305 Can read or write

```{r}
frq(hh$q_305) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 306 Ever attended school

```{r}
frq(hh$q_306) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 307 Reason never attended school

```{r}
frq(hh$q_307) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 308 Highest education attained

```{r}
frq(hh$q_308) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 309 Marital status

```{r}
frq(hh$q_309) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

## 314 Economic activity of household member

```{r}
frq(hh$q_314) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

What proportion of households

```{r}

```

## 315 Vaccinated for measles

```{r}
frq(hh$q_315) %>%
  data.frame() %>%
  select(3:5) %>%
  gt()
```

# Household Income and Consumption

## Overall

```{r}
inc_ov_tmp <- svyrdat %>%
  group_by() %>%
  summarize(crop_production=survey_mean(q_401_a_bin),
            cattle_production = survey_mean(q_401_b_bin),
            goat_production = survey_mean(q_401_c_bin),
            sheep_production = survey_mean(q_401_d_bin),
            fishing = survey_mean(q_401_e_bin),
            Agwage_within = survey_mean(q_401_f_bin),
            Agwage_without = survey_mean(q_401_g_bin),
            nonAgwage_within = survey_mean(q_401_h_bin),
            nonAgwage_without = survey_mean(q_401_i_bin),
            salary = survey_mean(q_401_j_bin),
            bush_products = survey_mean(q_401_k_bin),
            honey = survey_mean(q_401_l_bin),
            petty_trade_other = survey_mean(q_401_m_bin),
            petty_trade_own = survey_mean(q_401_n_bin),
            ownbiz_ag = survey_mean(q_401_o_bin),
            ownbiz_nonag = survey_mean(q_401_p_bin),
            rent = survey_mean(q_401_q_bin),
            remit = survey_mean(q_401_r_bin),
            gifts = survey_mean(q_401_s_bin),
            safety_net = survey_mean(q_401_t_bin))

```

```{r}
ov_cols <- seq_len(40) %% 2

inc_ov_mn <- inc_ov_tmp[, ov_cols==T] %>%
    pivot_longer(cols=1:20,
               names_to="income_source",
               values_to="Percent") %>%
  mutate(inc_lab=inc_labs) %>%
  relocate(inc_lab, .after=income_source)

inc_ov_se <- inc_ov_tmp[,ov_cols==F] %>%
  pivot_longer(cols=1:20,
               names_to="income_source",
               values_to="se")

inc_ov <- inc_ov_mn %>%
  bind_cols(inc_ov_se[,2]) %>%
  mutate(margin=se*1.96,
         lower=Percent-margin,
         upper=Percent+margin)

inc_gt <- inc_ov %>%
  select(-1, -4) %>%
  arrange(desc(Percent)) %>%
  gt() %>%
  fmt_percent(2:5,
              decimals=1) %>%
  cols_label(inc_lab="Income source") %>%
  tab_source_note("Survey instsrument items 401a-t")


inc_gt

```

## By county

### Long format, with confidence intervals

```{r}
inc_cnty_tmp <- svyrdat %>%
  group_by(county) %>%
  summarize(crop_production=survey_mean(q_401_a_bin),
            cattle_production = survey_mean(q_401_b_bin),
            goat_production = survey_mean(q_401_c_bin),
            sheep_production = survey_mean(q_401_d_bin),
            fishing = survey_mean(q_401_e_bin),
            Agwage_within = survey_mean(q_401_f_bin),
            Agwage_without = survey_mean(q_401_g_bin),
            nonAgwage_within = survey_mean(q_401_h_bin),
            nonAgwage_without = survey_mean(q_401_i_bin),
            salary = survey_mean(q_401_j_bin),
            bush_products = survey_mean(q_401_k_bin),
            honey = survey_mean(q_401_l_bin),
            petty_trade_other = survey_mean(q_401_m_bin),
            petty_trade_own = survey_mean(q_401_n_bin),
            ownbiz_ag = survey_mean(q_401_o_bin),
            ownbiz_nonag = survey_mean(q_401_p_bin),
            rent = survey_mean(q_401_q_bin),
            remit = survey_mean(q_401_r_bin),
            gifts = survey_mean(q_401_s_bin),
            safety_net = survey_mean(q_401_t_bin))
```

```{r}
cnty_cols <- seq_len(41) %% 2

inc_cnty_mn <- inc_cnty_tmp[, cnty_cols==F] %>%
  mutate(county=county_key$county) %>%
  relocate(county, .before=1) %>%
  pivot_longer(cols=2:21,
               names_to="income_source",
               values_to="Percent") %>%
  mutate(inc_lab = rep(inc_labs, 13))

inc_cnty_se <- inc_cnty_tmp[,cnty_cols==T] %>%
  pivot_longer(cols=2:21,
               names_to="income_source",
               values_to="se")

inc_cnty <- inc_cnty_mn %>%
  bind_cols(inc_cnty_se[,3]) %>%
  mutate(margin=se*1.96,
         lower=Percent-margin,
         upper=Percent+margin) %>%
  relocate(inc_lab, .after=income_source)

#Reactable with filters for county and income source

inc_cnty_obj <- inc_cnty %>% 
  select(-2, -5, -6) 

data_inc_cnty_obj <- SharedData$new(inc_cnty_obj)

bscols(
  widths = c(3, 9)
  , list(filter_select("county"
                       , "County"
                       , data_inc_cnty_obj
                       , ~county)
         ,filter_select("inc_lab"
                       , "Income source"
                       , data_inc_cnty_obj
                       , ~inc_lab))
  , reactable(data_inc_cnty_obj, showPageSizeOptions = T, highlight = T, columns = list(
    county = colDef(name = "County")
    , inc_lab = colDef(name = "Income source", minWidth = 150)
    , Percent = colDef(name = "Percent"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , lower = colDef(name = "Lower"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , upper = colDef(name = "Upper"
                     , format = colFormat(percent = T
                                          , digits = 1))
  )))

```

### Wide format to better show income source across counties

```{r}

inc_cnty_wide <- inc_cnty %>%
  select(1,3,4) %>%
  as.data.frame() %>%
  pivot_wider(names_from=county,
              values_from=Percent)

#Reactable with filter on Income source
data_inc_cnty_wide <- SharedData$new(inc_cnty_wide)

bscols(
  widths = c(3, 9)
  , list(filter_select("inc_lab"
                       , "Income source"
                       , data_inc_cnty_wide
                       , ~inc_lab))
  , reactable(data_inc_cnty_wide, showPageSizeOptions = T, highlight = T,  columns = list(
    inc_lab = colDef(name = "Income source"
                     , minWidth = 150
                     , sticky = "left"
                     , style = list(borderRight = "1px solid #eee"),
      headerStyle = list(borderRight = "1px solid #eee"))
    , Akobo = colDef(name = "Akobo"
                       , format = colFormat(percent = T, digits = 1))
    , Baliet = colDef(name = "Baliet"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Budi = colDef(name = "Budi"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Duk = colDef(name = "Duk"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , "Jur River" = colDef(name = "Jur River"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , "Kapoeta North" = colDef(name = "Kapoeta North"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Leer = colDef(name = "Leer"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Mayendit = colDef(name = "Mayendit"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Paynijar = colDef(name = "Paynijar"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Pibor = colDef(name = "Pibor"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Ulang = colDef(name = "Ulang"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Uror = colDef(name = "Uror"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Wau = colDef(name = "Wau"
                     , format = colFormat(percent = T
                                          , digits = 1))
  )))


#inc_cnty_wide_gt <- inc_cnty_wide %>%
#  gt() %>%
 # fmt_percent(2:14,
 #             decimals=0) %>%
 # cols_label(inc_lab="Income source")

#inc_cnty_wide_gt
```

## By reported conflicts

```{r}
inc_ov_tmp <- svyrdat %>%
  group_by() %>%
  summarize(crop_production=survey_mean(q_401_a_bin),
            cattle_production = survey_mean(q_401_b_bin),
            goat_production = survey_mean(q_401_c_bin),
            sheep_production = survey_mean(q_401_d_bin),
            fishing = survey_mean(q_401_e_bin),
            Agwage_within = survey_mean(q_401_f_bin),
            Agwage_without = survey_mean(q_401_g_bin),
            nonAgwage_within = survey_mean(q_401_h_bin),
            nonAgwage_without = survey_mean(q_401_i_bin),
            salary = survey_mean(q_401_j_bin),
            bush_products = survey_mean(q_401_k_bin),
            honey = survey_mean(q_401_l_bin),
            petty_trade_other = survey_mean(q_401_m_bin),
            petty_trade_own = survey_mean(q_401_n_bin),
            ownbiz_ag = survey_mean(q_401_o_bin),
            ownbiz_nonag = survey_mean(q_401_p_bin),
            rent = survey_mean(q_401_q_bin),
            remit = survey_mean(q_401_r_bin),
            gifts = survey_mean(q_401_s_bin),
            safety_net = survey_mean(q_401_t_bin))

```

# Dietary diversity

Overall frequencies, ranked in descending order

```{r}
q403 <- svy_disag(svyrdat, "", q_403, "403","Cereals")
q404 <- svy_disag(svyrdat, "", q_404, "404","Roots/tubers")
q405 <- svy_disag(svyrdat, "", q_405, "405","Vitamin A vegetables")
q406 <- svy_disag(svyrdat, "", q_406, "406","Leafy greens")
q407 <- svy_disag(svyrdat, "", q_407, "407","Other vegetables")
q408 <- svy_disag(svyrdat, "", q_408, "408","Vitamin A fruits")
q409 <- svy_disag(svyrdat, "", q_409, "409","Other fruits")
q410 <- svy_disag(svyrdat, "", q_410, "410","Organ meat")
q411 <- svy_disag(svyrdat, "", q_411, "411","Domesticated meat")
q412 <- svy_disag(svyrdat, "", q_412, "412","Bush meat")
q413 <- svy_disag(svyrdat, "", q_413, "413","Eggs")
q414 <- svy_disag(svyrdat, "", q_414, "414","Fish")
q415 <- svy_disag(svyrdat, "", q_415, "415","Legumes")
q416 <- svy_disag(svyrdat, "", q_416, "416","Milk products")
q417 <- svy_disag(svyrdat, "", q_417, "417","Oil and fats")
q418 <- svy_disag(svyrdat, "", q_418, "418","Sweets")
q419 <- svy_disag(svyrdat, "", q_419, "419","Spices/condiments")

diet_ov <- bind_rows(q403,
                       q404,
                       q405,
                       q406,
                       q407,
                       q408,
                       q409,
                       q410,
                       q411,
                       q412,
                       q413,
                       q414,
                       q415,
                       q416,
                       q417,
                       q418,
                       q419) %>%
  select(Item=var_name,
         Food=label,
         Percent=Value, lower, upper) %>%
  arrange(desc(Percent))

write_csv(diet_ov, here("output/tables/food insecurity/diet items overall.csv"))

#gtsave(diet_ov_gt, here("output/tables/food insecurity/diet items overall.rtf"))

diet_ov_gt <- diet_ov %>%
  gt() %>%
  fmt_percent(3:5,
              decimals=1)

diet_ov_gt

```

## Dietary diversity by county

```{r}
q403_cnty <- svy_disag(svyrdat, county, q_403, "403","Cereals")
q404_cnty <- svy_disag(svyrdat, county, q_404, "404","Roots/tubers")
q405_cnty <- svy_disag(svyrdat, county, q_405, "405","Vitamin A vegetables")
q406_cnty <- svy_disag(svyrdat, county, q_406, "406","Leafy greens")
q407_cnty <- svy_disag(svyrdat, county, q_407, "407","Other vegetables")
q408_cnty <- svy_disag(svyrdat, county, q_408, "408","Vitamin A fruits")
q409_cnty <- svy_disag(svyrdat, county, q_409, "409","Other fruits")
q410_cnty <- svy_disag(svyrdat, county, q_410, "410","Organ meat")
q411_cnty <- svy_disag(svyrdat, county, q_411, "411","Domesticated meat")
q412_cnty <- svy_disag(svyrdat, county, q_412, "412","Bush meat")
q413_cnty <- svy_disag(svyrdat, county, q_413, "413","Eggs")
q414_cnty <- svy_disag(svyrdat, county, q_414, "414","Fish")
q415_cnty <- svy_disag(svyrdat, county, q_415, "415","Legumes")
q416_cnty <- svy_disag(svyrdat, county, q_416, "416","Milk products")
q417_cnty <- svy_disag(svyrdat, county, q_417, "417","Oil and fats")
q418_cnty <- svy_disag(svyrdat, county, q_418, "418","Sweets")
q419_cnty <- svy_disag(svyrdat, county, q_419, "419","Spices/condiments")

diet_cnty <- bind_rows(q403_cnty,
                       q404_cnty,
                       q405_cnty,
                       q406_cnty,
                       q407_cnty,
                       q408_cnty,
                       q409_cnty,
                       q410_cnty,
                       q411_cnty,
                       q412_cnty,
                       q413_cnty,
                       q414_cnty,
                       q415_cnty,
                       q416_cnty,
                       q417_cnty,
                       q418_cnty,
                       q419_cnty)

write_csv(diet_cnty, here("output/tables/food insecurity/diet items by county.csv"))

# Object diet_cnty_obj is the object of "diet items by
# county.csv"

```

```{r}

# Object diet_cnty_obj is the object of "diet items by county.csv"

diet_cnty_obj <- read_csv(here("output/tables/food insecurity/diet items by county.csv")) %>% 
  select(county, label, Value, lower, upper)

data_diet_cnty_obj <- SharedData$new(diet_cnty_obj)

```

```{r}
bscols(
  widths = c(3, 9)
  , list(filter_select("county"
                       , "County"
                       , data_diet_cnty_obj
                       , ~county)
         ,filter_select("label"
                       , "Food Item"
                       , data_diet_cnty_obj
                       , ~label))
  , reactable(data_diet_cnty_obj, showPageSizeOptions = T, highlight = T, columns = list(
    county = colDef(name = "County")
    , label = colDef(name = "Food Item"
                     , minWidth = 150)
    , Value = colDef(name = "Percent"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , lower = colDef(name = "Lower"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , upper = colDef(name = "Upper"
                     , format = colFormat(percent = T
                                          , digits = 1))
  )))

```

# Food insecurity

## Food insecure behavior in previous 12 months

```{r}

q422 <- svy_disag(svyrdat, "", q_422, "worried", "Worried about not enough to eat") %>%
  select(4,5,2,6,7)

#q422

q423 <- svy_disag(svyrdat, "", q_423, "unhealthy", "Unable to eat healthy") %>%
  select(4,5,2,6,7)

#q423

q424 <- svy_disag(svyrdat, "", q_424, "few_foods", "Ate few kinds of foods") %>%
  select(4,5,2,6,7)

#q424

q425 <- svy_disag(svyrdat, "", q_425, "skip", "Skipped a meal") %>%
  select(4,5,2,6,7)

#q425

q426 <- svy_disag(svyrdat, "", q_426, "ate_less", "Ate less than needed") %>%
  select(4,5,2,6,7)

#q426

q427 <- svy_disag(svyrdat, "", q_427, "no_food", "Did not have food") %>%
  select(4,5,2,6,7)

#q427

q428 <- svy_disag(svyrdat, "", q_428, "not_eat", "Did not eat") %>%
  select(4,5,2,6,7)

#q428

q429 <- svy_disag(svyrdat, "", q_429, "wholeday", "Went a day without eating") %>%
  select(4,5,2,6,7)

#q429

fies_items <- do.call(rbind,
                      list(q422,
                           q423,
                           q424,
                           q425,
                           q426,
                           q427,
                           q428,
                           q429))


#fies_items


```

```{r}
fies_items_gt <- fies_items %>%
  select(-1) %>%
  gt() %>%
  fmt_percent(2:4,
              decimals=1) %>%
  cols_label(label="In previous 12 months..",
             Value="Percent") %>%
  tab_source_note("Survey instrument items 422-429") #%>%
  #tab_source_note("Behavior in past 12 months")

fies_items_gt

#gtsave(fies_items_gt, here("output/tables/food insecurity/fies items.rtf"))
```

## Food insecure behavior in previous four weeks

```{r}

q430 <- svy_disag(svyrdat, "", q_430, "no_food", "No food in house") %>%
  select("In previous four weeks.."=5,Percent=2,6,7) %>%
  gt() %>%
  fmt_percent(2:4,
              decimals=1)

q430

```

```{r}

# need to use survey package due to presence of not asked

q431 <- svytable(~q_431,
                     svydat,
                     Ntotal=T) %>%
  as.data.frame() %>%
  mutate(Response=c("Rarely (1-2 times)",
                    "Sometimes (3-10 times)",
                    "Often (More than 10 times)")) %>%
  select(3,Percent=2) %>%
  gt() %>%
  fmt_percent(2,
              decimals=1) %>%
  cols_label(Response=html("How often no food in house<br>in previous four weeks?"))

q431
```

```{r}

q432 <- svy_disag(svyrdat, "", q_432, "slept_hungry", "Went to bed hungry") %>%
  select(5,Percent=2,6,7) %>%
  gt() %>%
  fmt_percent(2:4,
              decimals=1) %>%
  cols_label(label="In the previous four weeks..")

q432

```

```{r}

# need to use survey package due to presence of not asked

q433 <- svytable(~q_433,
                     svydat,
                     Ntotal=T) %>%
  as.data.frame() %>%
  mutate(Response=c("Rarely (1-2 times)",
                    "Sometimes (3-10 times)",
                    "Often (More than 10 times)")) %>%
  select(3,Percent=2) %>%
  gt() %>%
  fmt_percent(2,
              decimals=1) %>%
  cols_label(Response=html("How often went to bed<br>hungry in past four weeks?"))

q433
```

```{r}
q434 <- svy_disag(svyrdat, "", q_434, "fast", "Went whole day without eating") %>%
  select(5,Percent=2,6,7) %>%
  gt() %>%
  fmt_percent(2:4,
              decimals=1) %>%
  cols_label(label="In the previous four weeks..")

q434
```

```{r}

# need to use survey package due to presence of not asked

q435 <- svytable(~q_435,
                     svydat,
                     Ntotal=T) %>%
  as.data.frame() %>%
  mutate(Response=c("Rarely (1-2 times)",
                    "Sometimes (3-10 times)",
                    "Often (More than 10 times)")) %>%
  select(3,Percent=2) %>%
  gt() %>%
  fmt_percent(2,
              decimals=1) %>%
  cols_label(Response=html("How often went a whole day<br>without eating in past four weeks?"))

q435
```

# Household involvement in the community

## Community group participation

```{r}

grps_sum <- read_csv(here("output/tables/resilience/groups weighted.csv"))

grps_sum_gt <- grps_sum %>%
  gt()

grps_sum_gt
```

# Household shocks

Overall frequencies, ranked in descending order

```{r}

#Flooding
q436 <- ov_tab(design = svyrdat, var = q_436)

q436_cnty <- svy_disag(design = svyrdat, item = q_436, disaggregate = county, varname = "q436", label = "Floods")

#Drought
q439 <- ov_tab(design = svyrdat, var = q_439)

q439_cnty <- svy_disag(design = svyrdat, item = q_439, disaggregate = county, varname = "q439", label = "Drought")

#Erosion
q442 <- ov_tab(design = svyrdat, var = q_442)

q442_cnty <- svy_disag(design = svyrdat, item = q_442, disaggregate = county, varname = "q442", label = "Erosion")

#Loss of land
q445 <- ov_tab(design = svyrdat, var = q_445)

q445_cnty <- svy_disag(design = svyrdat, item = q_445, disaggregate = county, varname = "q445", label = "Loss of land")

#Increase in food prices
q448 <- ov_tab(design = svyrdat, var = q_448)

q448_cnty <- svy_disag(design = svyrdat, item = q_448, disaggregate = county, varname = "q448", label = "Increase in food prices")

#Theft
q451 <- ov_tab(design = svyrdat, var = q_451)

q451_cnty <- svy_disag(design = svyrdat, item = q_451, disaggregate = county, varname = "q451", label = "Theft")

#No crop inputs
q455 <- ov_tab(design = svyrdat, var = q_455)

q455_cnty <- svy_disag(design = svyrdat, item = q_455, disaggregate = county, varname = "q455", label = "No crop inputs")

#Crop disease
q458 <- ov_tab(design = svyrdat, var = q_458)

q458_cnty <- svy_disag(design = svyrdat, item = q_458, disaggregate = county, varname = "q458", label = "Crop disease")

#Crop pests
q461 <- ov_tab(design = svyrdat, var = q_461)

q461_cnty <- svy_disag(design = svyrdat, item = q_461, disaggregate = county, varname = "q461", label = "Crop pests")

#Crop theft
q464 <- ov_tab(design = svyrdat, var = q_464)

q464_cnty <- svy_disag(design = svyrdat, item = q_464, disaggregate = county, varname = "q464", label = "Crop theft")

#No livestock inputs
q468 <- ov_tab(design = svyrdat, var = q_468)

q468_cnty <- svy_disag(design = svyrdat, item = q_468, disaggregate = county, varname = "q468", label = "No livestock inputs")

#Livestock disease
q471 <- ov_tab(design = svyrdat, var = q_471)

q471_cnty <- svy_disag(design = svyrdat, item = q_471, disaggregate = county, varname = "q471", label = "Livestock disease")

#Livestock theft
q474 <- ov_tab(design = svyrdat, var = q_474)

q474_cnty <- svy_disag(design = svyrdat, item = q_474, disaggregate = county, varname = "q474", label = "Livestock theft")

#Unable to sell
q477 <- ov_tab(design = svyrdat, var = q_477)

q477_cnty <- svy_disag(design = svyrdat, item = q_477, disaggregate = county, varname = "q477", label = "Unable to sell")

#Illness in household
q480 <- ov_tab(design = svyrdat, var = q_480)

q480_cnty <- svy_disag(design = svyrdat, item = q_480, disaggregate = county, varname = "q480", label = "Illness in household")

#Death in household
q484 <- ov_tab(design = svyrdat, var = q_484)

q484_cnty <- svy_disag(design = svyrdat, item = q_484, disaggregate = county, varname = "q484", label = "Death in household")

#Shocks overall frequencies
shocks_ov <- bind_rows(q436,
                       q439,
                       q442,
                       q445,
                       q448,
                       q451,
                       q455,
                       q458,
                       q461,
                       q464,
                       q468,
                       q471,
                       q474,
                       q477,
                       q480,
                       q484) %>% 
  mutate(Shocks = shock_labs) %>% 
  relocate(Shocks, .before=prop) %>% 
  select(Shocks,
         Percent=prop
         , margin
         , lower
         , upper) %>% 
  arrange(desc(Percent))

write_csv(shocks_ov, here("output/tables/shocks/shocks overall.csv"))

#gtsave(diet_ov_gt, here("output/tables/food insecurity/diet items overall.rtf"))

shocks_ov_gt <- shocks_ov %>%
  gt() %>%
  fmt_percent(2:5,
              decimals=1)

shocks_ov_gt
```

## Household shocks by county

```{r}
shocks_ov_cnty <- bind_rows(q436_cnty,
                       q439_cnty,
                       q442_cnty,
                       q445_cnty,
                       q448_cnty,
                       q451_cnty,
                       q455_cnty,
                       q458_cnty,
                       q461_cnty,
                       q464_cnty,
                       q468_cnty,
                       q471_cnty,
                       q474_cnty,
                       q477_cnty,
                       q480_cnty,
                       q484_cnty)  %>% 
  select(County = county
         , Shocks = label
         , Percent = Value
         , Lower = lower
         , Upper = upper)
   
#reactable for shocks by county
data_shocks_ov_cnty <- SharedData$new(shocks_ov_cnty)

bscols(
  widths = c(3,9)
  , list(filter_select("County"
                       , "County"
                       , data_shocks_ov_cnty
                       , ~County)
         , filter_select("Shocks"
                         , "Shocks"
                         , data_shocks_ov_cnty
                         , ~Shocks))
  , reactable(data_shocks_ov_cnty, showPageSizeOptions = T
              , highlight = T
              , columns = list(County = colDef(name = "County")
                               , Shocks = colDef(minWidth = 150)
                               , Percent = colDef(format = colFormat(percent = T
                                                                     , digits = 1))
                               , Lower = colDef(format = colFormat(percent = T
                                                                     , digits = 1))
                               , Upper = colDef(format = colFormat(percent = T
                                                                     , digits = 1))
              )))

 


```

### Wide format to better show shocks across counties

```{r}
shocks_cnty_wide <- shocks_ov_cnty %>%
  select(1, 2, 3) %>% 
  as.data.frame() %>% 
  pivot_wider(names_from=County
              , values_from=Percent)

#Reactable with filter on Shocks
data_shocks_cnty_wide <- SharedData$new(shocks_cnty_wide)

bscols(
  widths= c(3,9)
  , list(filter_select("Shocks"
                       , "Shocks"
                       , data_shocks_cnty_wide
                       , ~Shocks))
  , reactable::reactable(data_shocks_cnty_wide, showPageSizeOptions = T
              , highlight = T
              , columns = list(Shocks = colDef(name = "Shocks"
                , minWidth = 150
                , sticky = "left" 
                , style = list(borderRight = "1px solid #eee")                                   , headerStyle = list(borderRight = "1px solid #eee"))
                
                               , Akobo = colDef(name = "Akobo"
                       , format = colFormat(percent = T, digits = 1))
    , Baliet = colDef(name = "Baliet"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Budi = colDef(name = "Budi"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Duk = colDef(name = "Duk"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , "Jur River" = colDef(name = "Jur River"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , "Kapoeta North" = colDef(name = "Kapoeta North"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Leer = colDef(name = "Leer"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Mayendit = colDef(name = "Mayendit"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Paynijar = colDef(name = "Paynijar"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Pibor = colDef(name = "Pibor"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Ulang = colDef(name = "Ulang"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Uror = colDef(name = "Uror"
                     , format = colFormat(percent = T
                                          , digits = 1))
    , Wau = colDef(name = "Wau"
                     , format = colFormat(percent = T
                                          , digits = 1)) 
                               )))

```
