---
title: "Social capital explore"
author: "Dan Killian"
date: "11/17/2021"
output: 
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    fig.caption: true
    code_folding: hide
    df_print: kable
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
# standard figure size and generate clean output
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)

source(here("code/00 South Sudan resilience - prep.R"))

#dat <- dat %>%
#  mutate(id=1:6564)

```

# Introduction

The South Sudan Monitoring and Evaluation Support Project (MESP) is conducting a household resilience survey in 13 counties. The purpose of this household survey is to obtain baseline data in the target areas for the indicators included in the Mission's Performance Management Plan (PMP) and the Community Roadmap, in support of USAID/South Sudan's Strategic Framework (2020-2024).

MESP has completed data collection in six counties, and as of October 2021 is carrying out data collection in the remaining seven counties. The study team is currently reviewing the data from six counties in advance of analysis of the full set of 13 counties. This document is one of a series of documents to review various measures and indices relating to resilience.

# Social capital

```{r}
frq(dat$bonding_capital_raw)
```

```{r}
frq(dat$bonding_capital_score)
```


```{r}
socap <- dat %>%
  select(q_490, rc_q_491, q_494, rc_q_495,
         q_492, rc_q_493, q_496, rc_q_497)


socap_temp <- svyrdat %>%
  summarize(q490 = survey_mean(q_490, na.rm=T),
            q491 = survey_mean(rc_q_491, na.rm=T),
            q494 = survey_mean(q_494, na.rm=T),
            q495 = survey_mean(rc_q_495, na.rm=T),
            q492 = survey_mean(q_492, na.rm=T),
            q493 = survey_mean(rc_q_493, na.rm=T),
            q496 = survey_mean(q_496, na.rm=T),
            q497 = survey_mean(rc_q_497, na.rm=T))

socap_temp

socap_mn <- socap_temp %>%
  select(!contains("se")) %>%
  melt() %>%
  mutate(type = c(rep("Bonding", 4), rep("Bridging", 4)),
         item = c("Able to lean on relatives\nin community (Bonding)",
                  "Able to help relatives\nin community (Bonding)",
                  "Able to lean on non-relatives\nin community (Bonding)",
                  "Able to help non-relatives\nin community (Bonding)",
                  "Able to lean on relatives\noutside community (Bridging)",
                  "Able to help relatives\noutside community (Bridging)",
                  "Able to lean on non-relatives\n outside community (Bridging)",
                  "Able to help non-relatives\n outside community (Bridging)")) %>%
  select(1,3,4,2)
         

socap_se <- socap_temp %>%
  select(contains("se")) %>%
  melt() %>%
  rename(se=value)

socap_se

socap_sum <- socap_mn %>%
  cbind(socap_se[,2]) %>%
  rename(percent=value,
         se = 5) %>%
  mutate(lower=percent-1.96*se,
         upper=percent+1.96*se)

socap_sum

write_csv(socap_sum, here("output/tables/social capital/social capital weighted.csv"))

```


```{r}
ggplot(socap_sum, aes(x=percent, y=fct_reorder(item, percent))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, size=1, color=medium_blue, ) + 
  geom_label(aes(label=paste(round(percent,2)*100, "%", sep="")), 
             size=5, color="white", fill=medium_blue, label.padding = unit(.17, "lines")) +
  scale_x_continuous(labels=percent,
                     limits=c(0,1),
                     breaks=seq(0,1,.2)) + 
  labs(x="",
       y="")

ggsave(here("output/viz/social capital/socap items weighted.png"),
       device="png",
       type="cairo",
       height=5,
       width=7)
```


```{r}
ggplot(dat, aes(bonding_capital_raw)) + 
  geom_bar()

```


```{r}
describe(dat$bridging_capital_raw)

bond_mn <- svyrdat %>%
  summarize(bond=survey_mean(bonding_capital_raw, na.rm=T)) %>%
#            bridge = survey_mean(bridging_capital_raw, na.rm=T)) %>%
  mutate(lower=bond-1.96*bond_se,
         upper=bond+1.96*bond_se,
         measure="Bonding",
         y=1) %>%
  rename(value=bond,
         se=2)

bond_mn
```

```{r}
describe(dat$bridging_capital_raw)

bridge_mn <- svyrdat %>%
  summarize(bridge = survey_mean(bridging_capital_raw, na.rm=T)) %>%
  mutate(lower=bridge-1.96*bridge_se,
         upper=bridge+1.96*bridge_se,
         measure="Bridging",
         y=1.5) %>%
  rename(value=bridge,
         se=2)

bridge_mn
```

```{r}
socap_mn <- bond_mn %>%
  rbind(bridge_mn) %>%
  relocate(5, .before=value)

socap_mn
```

```{r}
a <- ggplot(dat, aes(bonding_capital_raw, weight=final_wt1)) + 
  geom_bar(width=.2, fill="dodgerblue2") + 
#  geom_vline(xintercept=3.9, size=1, color="darkgoldenrod2") + 
  geom_vline(xintercept=1.6, size=1, color="darkgoldenrod2") +
  scale_x_continuous(breaks=0:4) + 
  scale_y_continuous(limits=c(0,1e5)) +
  labs(x="",
       y="") +
  theme(axis.text.y=element_blank())

,
        axis.text.x=element_blank())
a
```

```{r}
b <- ggplot(socap_mn, aes(value, reorder(measure, value))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, color=medium_blue) +
  #geom_hline(yintercept=1, color=light_blue, size=1) +
  geom_segment(aes(x=0, xend=6, y=c(1,2), yend=c(1,2)), color=light_blue) + 
  geom_label(aes(label=round(value,1)), color="darkgoldenrod2", size=6) +
  scale_x_continuous(limits=c(0, 4),
                     breaks=0:4) +
#  scale_y_discrete(limits=c(0,4),
#                   breaks=0:4) +
  labs(x="",
       y="") +
  theme(axis.text.x=element_blank())

b

ggsave(here("output/viz/shocks/arssi weighted.png"),
       device="png",
       type="cairo",
       height=1.2,
       width=3)
```

```{r}
d <- ggplot(dat, aes(bridging_capital_raw, weight=final_wt1)) + 
  geom_bar(width=.2, fill="dodgerblue2") + 
  geom_vline(xintercept=1.3, size=1, color="darkgoldenrod2") + 
#  geom_vline(xintercept=4, size=1, color="turquoise") +
  scale_x_continuous(breaks=0:4) + 
  scale_y_continuous(limits=c(0,1e5)) + 
  labs(x="",
       y="") +
  theme(axis.text.y=element_blank())
,
        axis.text.x=element_blank())
d
```


```{r}
library(patchwork)
a/b/d

ggsave(here("output/viz/social capital/socap means weighted.png"),
       type="cairo",
       device="png",
       height=4,
       width=7)
```


```{r}
ltm_bnd <- ltm(socap[,1:4] ~ z1)
ltm_bnd
```

```{r}
ltm_brdg <- ltm(socap[,5:8] ~ z1)
ltm_brdg
```

```{r}
ltm_coh <- ltm(socap ~ z1)
ltm_coh
```


```{r}
fa.parallel(socap[,1:4],
            cor="tet")
```

2 factors, 1 component

```{r}
prin_bond <- principal(socap[,1:4],
                       cor="tet")
prin_bond
```

```{r}
prin_bond_scrs <- prin_bond$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(bonding_comp = prin_bond_scrs$PC1,
         bonding_comp_resc = unlist(rescale(bonding_comp, c(0,100))))

ggplot(dat, aes(bonding_comp)) + 
  geom_density()
```

```{r}
fa_bond <- fa(socap[,1:4],
              cor="tet",
              #scores="tenBerge",
              fm="ml")
fa_bond
```

```{r}
fa_bond_scrs <- fa_bond$scores %>%
  unlist() %>%
  as.data.frame()

str(fa_bond_scrs)

dat <- dat %>%
  mutate(bonding_fac = fa_bond_scrs$ML1,
         bonding_fac_resc = unlist(scales::rescale(bonding_fac, c(0,100))),
         bonding_fac_resc = as.numeric(bonding_fac_resc))

ggplot(dat, aes(bonding_fac)) + 
  geom_density()
```

```{r}
describe(dat$bonding_fac_resc)

bond_resc_mn <- svyrdat %>%
  summarize(bond=survey_mean(bonding_fac_resc, na.rm=T)) %>%
  mutate(lower=bond-1.96*bond_se,
         upper=bond+1.96*bond_se,
         measure="")

bond_resc_mn
```

```{r}
fa.parallel(socap[,5:8],
            cor="tet")
```
2 factors, 1 component

```{r}
prin_bridge <- principal(socap[,5:8],
                       cor="tet")
prin_bridge
```

```{r}
prin_bridge_scrs <- prin_bridge$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(bridging_comp = prin_bridge_scrs$PC1,
         bridging_comp_resc = unlist(rescale(bridging_comp, c(0,100)))) %>%
  mutate(bridging_comp_resc = as.numeric(bridging_comp_resc))

ggplot(dat, aes(bridging_comp)) + 
  geom_density()
```

```{r}
fa_bridge <- fa(socap[,5:8],
              cor="tet",
              #scores="tenBerge",
              fm="ml")
fa_bridge
```

```{r}
fa_bridge_scrs <- fa_bridge$scores %>%
  unlist() %>%
  as.data.frame()

str(fa_bridge_scrs)

dat <- dat %>%
  mutate(bridging_fac = fa_bridge_scrs$ML1,
         bridging_fac_resc = as.vector(scales::rescale(bridging_fac, c(0,100)))) %>%
  mutate(bridging_fac_resc = as.numeric(bridging_fac_resc))

ggplot(dat, aes(bridging_fac)) + 
  geom_density()
```

```{r}
describe(dat$bridging_fac_resc)

bridge_resc_mn <- svyrdat %>%
  summarize(bridge=survey_mean(bridging_fac_resc, na.rm=T)) %>%
  mutate(lower=bridge-1.96*bridge_se,
         upper=bridge+1.96*bridge_se,
         measure="")

bridge_resc_mn
```


```{r}
fa.parallel(socap, 
            cor="tet")
```

4 factors, 1 component

```{r}
prin_socap <- principal(socap,
                        cor="tet")
prin_socap
```

81 percent of variance captured

```{r}

prin_bond_brdg <- dat %>%
  select(bonding_comp, bridging_comp) %>%
  principal()

prin_bond_brdg
```

```{r}

prin_bond_brdg_scrs <- prin_bond_brdg$scores %>%
  unlist() %>%
  as.data.frame()
  
dat <- dat %>%
  mutate(cohesion_comp_latent = prin_bond_brdg_scrs$PC1,
         cohesion_comp_latent_resc = scales::rescale(cohesion_comp_latent, c(0,100)))

ggplot(dat, aes(cohesion_comp_latent)) + 
  geom_density()
describe(dat$cohesion_comp_latent)
```

```{r}
describe(dat$cohesion_comp_resc)

asp_resc_mn <- svyrdat %>%
  summarize(Asp=survey_mean(aspirations_comp_resc, na.rm=T)) %>%
  mutate(lower=Asp-1.96*Asp_se,
         upper=Asp+1.96*Asp_se,
         measure="")

asp_resc_mn
```

```{r}
library(scales)
prin_socap_scrs <- prin_socap$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(cohesion_sum = rowSums(socap),
         cohesion_comp = prin_socap_scrs$PC1,
         cohesion_comp_resc = scales::rescale(cohesion_comp, to=c(0,100)))


ggplot(dat, aes(cohesion_comp)) + 
  geom_density()

```

```{r}
cohesion_fac <- dat %>%
  select(bonding_fac,
         bridging_fac) %>%
  fa(scores="tenBerge",
     fm="ML")
cohesion_fac

```

```{r}
cohesion_fac_scrs <- cohesion_fac$scores %>%
  unlist() %>%
  as.data.frame()

dat <- dat %>%
  mutate(cohesion_latent = cohesion_fac_scrs$ML1,
         cohesion_latent_resc = scales::rescale(cohesion_latent, c(0,100)))

ggplot(dat, aes(cohesion_latent)) + 
  geom_density()
```

```{r}

cohesion_latent_temp <- svyrdat %>%
  summarize(cohesion_latent = survey_mean(cohesion_latent_resc, na.rm=T),
            bonding_fac = survey_mean(bonding_fac_resc, na.rm=T),
            bridging_fac = survey_mean(bridging_fac_resc, na.rm=T)) 

cohesion_latent_temp

cohesion_latent_mn <- cohesion_latent_temp %>%
  select(!contains("se")) %>%
  melt()

cohesion_latent_mn

cohesion_latent_se <- cohesion_latent_temp %>%
  select(contains("se")) %>%
  melt() %>%
    rename(se=2)

cohesion_latent_se

cohesion_latent <- cohesion_latent_mn %>%
  cbind(cohesion_latent_se[,2]) %>%
  rename(se=3) %>%
  mutate(lower=value-1.96*se,
         upper=value+1.96*se,
         measure=c("Cohesion", "Bonding capital","Bridging capital")) 
         
cohesion_latent

write_csv(cohesion_latent, here("output/tables/cohesion weighted.csv"))

```

```{r}

ggplot(cohesion_latent, aes(value, reorder(measure, value))) + 
  geom_errorbar(aes(xmin=lower, xmax=upper), width=0, color=medium_blue) +
  #geom_hline(yintercept=1, color=light_blue, size=1) +
  geom_segment(aes(x=0, xend=100, y=1:3, yend=1:3), color=light_blue) + 
  geom_label(aes(label=round(value,1)), color=medium_blue, size=6, label.padding=unit(.15, "lines")) +
  scale_x_continuous(limits=c(0, 100),
                     breaks=seq(0,100,25)) +
#  scale_y_discrete(limits=c(0,4),
#                   breaks=0:4) +
  labs(x="",
       y="") 
+
  theme(axis.text.x=element_blank())

b

ggsave(here("output/viz/social capital/cohesion capital rescale.png"),
       device="png",
       type="cairo",
       height=2,
       width=4)
```

```{r}
describe(dat$agency_latent_resc)
describe(dat$shock_exposure_index)
```

## Shocks and agency, cohesion

```{r}
l1 <- svyglm(shock_exposure_index ~ agency_latent + cohesion_latent,
             design=svydat)

summary(l1)

```

```{r}
l2 <- svyglm(shock_exposure_index ~ agency_latent + cohesion_latent + 
               household_members + urban + as.factor(hh_head_sex),
             design=svydat)

summary(l2)

```

```{r}
l3 <- svyglm(shock_exposure_index ~ agency_latent + cohesion_latent + 
               household_members + urban + conflict + as.factor(hh_head_sex) + as.factor(county),
             design=svydat)

summary(l3)

```

```{r}

```

# Conflict

```{r}
l1 <- svyglm(conflict ~ shock_exposure_index + agency_latent + cohesion_latent +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l1)

```

```{r}
l2 <- svyglm(conflict ~ shock_exposure_index + agency_latent + bonding_fac + bridging_fac +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l2)

```

```{r}
l3 <- svyglm(trauma ~ shock_exposure_index + agency_latent + bonding_fac + bridging_fac +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l3)

```



# FIES


```{r}
l1 <- svyolr(ordered(fies_raw) ~ shock_exposure_index + conflict + agency_latent + cohesion_latent +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             method="probit",
             design=svydat)
summary(l1)

```

```{r}
l1 <- svyglm(fies_raw ~ shock_exposure_index + conflict + agency_latent + cohesion_latent +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l1)

```

# ARSSI 

```{r}

describe(dat$ab)

l1 <- svyglm(ability_recover ~ shock_exposure_index + conflict + agency_latent + cohesion_latent +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l1)

```

# Informal safety nets

```{r}

describe(dat$grp_latent)

l1 <- svyglm(grp_latent ~ shock_exposure_index + conflict + agency_latent + cohesion_latent +
               household_members + as.factor(hh_head_sex) + urban + as.factor(county),
             design=svydat)
summary(l1)

```

```{r}
l1 <- svyglm(cohesion_latent ~ as.factor(county) + as.factor(hh_head_sex) + urban,
             design=svydat)

summary(l1)

```


