---
title: "Food insecurity explore"
author: "Dan Killian"
date: "10/26/2021"
output: 
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    fig.caption: true
    code_folding: hide
    df_print: kable
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
# standard figure size and generate clean output
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)

source(here("code/00 South Sudan resilience - prep.R"))

dat <- read_dta(here("data/local/SSD resilience baseline prepared.dta")) %>%
  mutate(id=1:3563)

# frq_disag <- function(object, disaggregate, item, label, media) {
#   temp <- object %>%
#     group_by({{disaggregate}}) %>%
#     summarize(Percent=mean({{item}}, na.rm=T),
#               se=std.error({{item}}, na.rm=T)) %>%
#     mutate(var_name={{label}},
#            Media={{media}},
#            lower=Percent-1.96*se,
#            upper=Percent+1.96*se)
#   temp
# }

svy_disag <- function(design, disaggregate, item, label) {
  temp <- design %>%
    group_by({{disaggregate}}) %>%
    summarize(Value=survey_mean({{item}}, na.rm=T)) %>%
    mutate(item={{item}},
           label={{label}},
           lower=Value-1.96*se,
           upper=Value+1.96*se)
  temp
}


# svyrdat <- dat %>%
#   as_survey_design(ids = ea,
#                    strata=county,
#                    weights=final_wt1)
```

# Introduction

The South Sudan Monitoring and Evaluation Support Project (MESP) is conducting a household resilience survey in 13 counties. The purpose of this household survey is to obtain baseline data in the target areas for the indicators included in the Mission's Performance Management Plan (PMP) and the Community Roadmap, in support of USAID/South Sudan's Strategic Framework (2020-2024).

MESP has completed data collection in six counties, and as of October 2021 is carrying out data collection in the remaining seven counties. The study team is currently reviewing the data from six counties in advance of analysis of the full set of 13 counties. This document is one of a series of documents to review various measures and indices relating to resilience.

# Food insecurity 

Food insecurity is the lack of confidence that the household will consistently maintain the caloric and dietary needs of its members. The South Sudan resilience baseline asks questions about food insecurity across two different temporal windows: 12 months and four weeks. The following survey items address the issue of food insecurity.

```{r}

fies <- dat %>%
  select(q_422:q_429)

svy_disag <- function(design, disaggregate, item, varname, label) {
  temp <- design %>%
    group_by({{disaggregate}}) %>%
    summarize(Value=survey_mean({{item}}, na.rm=T)) %>%
    mutate(#item={{item}},
           var_name={{varname}},
           label={{label}},
           lower=Value-1.96*Value_se,
           upper=Value+1.96*Value_se)
  temp
}

q422 <- svy_disag(svyrdat, "", q_422, "worried", "Worried about not enough to eat") %>%
  select(4,5,2,6,7)

#q422

q423 <- svy_disag(svyrdat, "", q_423, "unhealthy", "Unable to eat healthy") %>%
  select(4,5,2,6,7)

#q423

q424 <- svy_disag(svyrdat, "", q_424, "few_foods", "Ate few kinds of foods") %>%
  select(4,5,2,6,7)

#q424

q425 <- svy_disag(svyrdat, "", q_425, "skip", "Skipped a meal") %>%
  select(4,5,2,6,7)

#q425

q426 <- svy_disag(svyrdat, "", q_426, "ate_less", "Ate less than needed") %>%
  select(4,5,2,6,7)

#q426

q427 <- svy_disag(svyrdat, "", q_427, "no_food", "Did not have food") %>%
  select(4,5,2,6,7)

#q427

q428 <- svy_disag(svyrdat, "", q_428, "not_eat", "Did not eat") %>%
  select(4,5,2,6,7)

#q428

q429 <- svy_disag(svyrdat, "", q_429, "fast", "Went a day without eating") %>%
  select(4,5,2,6,7)

#q429

fies_items <- do.call(rbind, 
                      list(q422,
                           q423,
                           q424,
                           q425,
                           q426,
                           q427,
                           q428,
                           q429))


fies_items

write.csv(fies_items, "output/tables/food insecurity/fies items.csv")

fies_items_gt <- fies_items %>%
  gt() %>%
  fmt_percent(3:5,
              decimals=1)
```

```{r echo=F, fig.cap="Items comprising Food Insecurity Experience Scale (FIES)"}
fies_items_gt

```
We can create an index value that is simply the sum of items the respondent agrees to. This has already been calculated under the variable 'fies_raw'. 

```{r}
frq(dat$fies_raw)
```
A great majority of respondents agreed with all eight items, raising questions about the suitability of this data for scale construction. We'll proceed to see what happens and to illustrate the methods. 

First, let's take a look at the conditional probabilities for each possible scale value. 



We can add transform the item proportions into odds and log-odds to help with further analysis. 

```{r}
fies_items <- fies_items %>%
  mutate(odds=Value/(1-Value),
         logits=log(odds)) %>%
  select(-(4:5))

fies_items
```
How well do the logits map to the original scale value of the sum of items? 

```{r}
ggplot(fies_items, aes())
```



```{r}
f2 <- dat %>%
  select(q_430:q_435)

head(f2)
map(f2, frq)
```




# Analytical models

## FAO models

```{r}
library(ltm)
library(eRm)
library(RM.weights)

names(dat)
names(fies_items)

rash <- fies_items %>%
  select(1:8)

rash <- dat %>%
  select(q_422:q_429) %>%
#  as.data.frame() %>%
  map(., as.numeric) %>%
  as.data.frame() %>%
  na.omit()

rash <- map(rash, as.numeric) %>%
  as.matrix()

str(rash)

rash2 <- dat %>%
  select(q_422:q_429, hh_wt)

head(rash)

r1 <- RM.w(rash)
str(rash)

r1
summary(r1)

```

```{r}
r1$b
```

# LTM package

```{r}
library(ltm)

descript(fies)

```
```{r}
plot(descript(fies))
```

## ltm

``` {r}

l1 <- ltm(fies ~ z1)
l1
summary(l1)
```

```{r}
plot(l1, type="ICC")
```

```{r}
plot(l1, type="IIC")
```
```{r}
plot(l1_scores, type="loadings")
```
```{r}
plot(l1, 
     type="IIC", 
     items=0)
```



```{r}
person.fit(l1)
```


```{r}

l1_scores <- factor.scores(l1)


l1_scores_dat <- l1_scores$score.dat

sum(l1_scores_dat$Obs)

ggplot(l1_scores_dat, aes(z1, weight=Obs)) + 
  geom_density() +
  scale_x_continuous(limits=c(-2.5,.5))

```
```{r}
plot(l1_scores)
```
```{r}

```



```{r}
describe(dat$fies)



```


## rasch 

```{r}
r1 <- rasch(fies)
summary(r1)
```

```{r}
coef(r1)
```
```{r}

```


# Dietary diversity 

```{r}

#frq(dat$fies_raw)

diet <- dat %>%
select(q_403:q_419)

fa.parallel(diet)

fa_diet_6 <- fa(diet,
nfactors=6)

fa_diet_6
```


```{r}
fa_diet_6_scores <- data.frame(fa_diet_6$scores) 

dat2 <- dat %>%
cbind(fa_diet_6_scores)

ggplot(dat2, aes(MR3, fies_raw)) + 
geom_point() + 
stat_smooth(method="lm")

```


```{r}
l1 <- lm(fies_raw ~ MR1 + MR2 + MR3 + MR4 + MR5 + MR6,
data=dat2)

summary(l1)
```

```{r}
inc <- dat %>%
select(q_401_a_bin,
q_401_b_bin,
q_401_c_bin,
q_401_d_bin,
q_401_e_bin,
q_401_f_bin,
q_401_g_bin,
q_401_h_bin,
q_401_i_bin,
q_401_j_bin,
q_401_k_bin,
q_401_j_bin,
q_401_k_bin,
q_401_l_bin,
q_401_m_bin,
q_401_n_bin,
q_401_o_bin,
q_401_p_bin,
q_401_q_bin,
q_401_r_bin,
q_401_s_bin,
q_401_t_bin,
q_401_u_bin)

str(inc)
head(inc)

fa.parallel(inc
, cor="tet")

```

```{r}
fa_inc_6 <- fa(inc,
nfactors=6)

fa_inc_6

```

