---
title: "South Sudan Resilience Baseline"
subtitle: "Responses to selected comments"
author: "Dan Killian"
toc: true
toc-depth: 3
number-sections: true
format: 
  html:
    code-fold: true
editor: visual
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(autodep=T, fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)
source("00 South Sudan resilience - prep.R")
```

# Background

# Comments

### pg 17, Brian Hilton

### Comment

There should be changes in food security between rainy season and dry season. Could we compare adjacent counties for example Budi and Kapoeta N. The second comparison could be Mayendit and Leer?

### Response

Compare food insecurity across counties:

```{r}

out <- dat %>%
  group_by(county) %>%
  summarize(food_insec=mean(fies_raw, na.rm=T),
            fies_se=std.error(fies_raw))

out



```

```{r}
m1 <- aov(fies_raw ~ as.factor(county), dat)
m1
summary(m1)
ranef(m1)
```

## 








pg 17, Brian Hilton













There should be changes in food security between rainy
season and dry season.  Could we compare
adjacent counties for example Budi and Kapoeta N.  The second comparison could be Mayendit and
Leer?
