---
title: "South Sudan resilience"
subtitle: "Trauma review"
author: "Dan Killian"
date: "1/7/2022"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    fig.caption: true
    code_folding: hide
    df_print: kable
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}

# standard figure size and generate clean output
knitr::opts_chunk$set(fig.height=4, fig.width=6, warning=FALSE, message=FALSE, cache=TRUE, error=T, echo=T)

library(here)

source(here("code/00 South Sudan resilience - prep.R"))

```


# Introduction

The South Sudan Monitoring and Evaluation Support Project (MESP) is conducting a household resilience survey in 13 counties. The purpose of this household survey is to obtain baseline data in the target areas for the indicators included in the Mission's Performance Management Plan (PMP) and the Community Roadmap, in support of USAID/South Sudan's Strategic Framework (2020-2024).

MESP has completed data collection in six counties, and as of October 2021 is carrying out data collection in the remaining seven counties. The study team is currently reviewing the data from six counties in advance of analysis of the full set of 13 counties. This document is one of a series of documents to review various measures and indices relating to resilience.

# Experience of trauma

The survey asks six questions pertaining to the incidence of trauma. The preparatory text explains that trauma occurs when distressing events cause stress that changes a person's thinking, feelings, behavior, interpersonal relationships, physical well-being, or functioning for daily activities. The following table shows these item frequencies.

```{r}
trauma <- dat %>%
  select(q_711,
         q_715,
         q_719,
         q_723,
         q_727,
         q_731)

dat <- dat %>%
  mutate(trauma_thoughts = case_when(q_711 == 1 ~ 1,
                                     TRUE ~ 0),
         trauma_feelings = case_when(q_715 == 1 ~ 1,
                                     TRUE ~ 0),
         trauma_behavior = case_when(q_719 == 1 ~ 1,
                                     TRUE ~ 0),
         trauma_relations = case_when(q_723 == 1 ~ 1,
                                     TRUE ~ 0),
         trauma_physical = case_when(q_727 == 1 ~ 1,
                                     TRUE ~ 0),
         trauma_function = case_when(q_731 == 1 ~ 1,
                                     TRUE ~ 0)) 

trauma <- dat %>%
  select(trauma_thoughts:trauma_function)

<<<<<<< HEAD
trauma_out <- trauma %>%
  summarize(trauma_thoughts=mean(trauma_thoughts))
=======
#trauma_out <- trauma %>%
#  summarize(trauma_thoughts=mean(trauma_thoughts))
>>>>>>> 53697d484cb70458c87d3338f2aaa536f3391614

trauma_out <- svyrdat %>%
  group_by() %>%
  summarize(trauma_thoughts=survey_mean(trauma_thoughts),
            trauma_feelings=survey_mean(trauma_feelings),
            trauma_behavior=survey_mean(trauma_behavior),
            trauma_relations=survey_mean(trauma_relations),
            trauma_physical=survey_mean(trauma_physical),
            trauma_function=survey_mean(trauma_function)) %>%
  select(1,3,5,7,9,11) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column("var_name") %>%
  mutate(item_num=c("q_711","q_715","q_719","q_723", "q_727","q_731"),
         Description=c("Problems with thinking", 
                       "Problems with emotions",
                       "Problems with behavior",
                       "Problems with relationships",
                       "Problems with physical symptoms",
                       "Problems with physical functioning")) %>%
  select(var_name, item_num, Description, Percent=V1) %>%
  arrange(desc(Percent))

trauma_out

<<<<<<< HEAD

```

=======
trauma_out_gt <- trauma_out %>%
  gt() %>%
  fmt_percent(4,
             decimals=1)

trauma_out_gt


```

```{r}

trauma_temp <- svyrdat %>%
  group_by() %>%
  summarize(trauma_thoughts=survey_mean(trauma_thoughts),
            trauma_feelings=survey_mean(trauma_feelings),
            trauma_behavior=survey_mean(trauma_behavior),
            trauma_relations=survey_mean(trauma_relations),
            trauma_physical=survey_mean(trauma_physical),
            trauma_function=survey_mean(trauma_function))


trauma_mn <- trauma_temp %>%
  select(!contains("se")) %>%
  t() %>%
  as.data.frame() %>%
  rownames_to_column("item") %>%
  rename(percent=V1)

trauma_mn

trauma_se <- trauma_temp %>%
  select(contains("se")) %>%
  t() %>%
  as.data.frame() %>%
#  rownames_to_column("conflict") %>%
  rename(se=V1)

trauma_se

trauma_sum <- trauma_mn %>%
  cbind(trauma_temp[,2]) %>%
  rename(se=3) %>%
  mutate(lower=percent-1.96*se,
         upper=percent+1.96*se,
         item_num=c("q_711","q_715","q_719","q_723", "q_727","q_731"),
         Description=c("Problems with thinking", 
                       "Problems with emotions",
                       "Problems with behavior",
                       "Problems with relationships",
                       "Problems with physical symptoms",
                       "Problems with physical functioning")) %>%
   select(1, 6:7, everything())

trauma_sum

write_csv(trauma_sum, here("output/tables/trauma items.csv"))

trauma_gt <- trauma_sum %>%
  select(-5) %>%
  gt() %>%
  fmt_percent(4:6, 
              decimals=1)

trauma_gt

gtsave(trauma_gt, here("output/tables/trauma items.rtf"))

```


>>>>>>> 53697d484cb70458c87d3338f2aaa536f3391614
A composite variable takes the value one if any of those symptoms were reported, zero otherwise. The incidence of this composite variable for exposure to trauma is 84 percent. 

```{r}
trauma_mn <- svyrdat %>%
  group_by() %>%
  summarize(trauma=survey_mean(trauma, na.rm=T))

trauma_mn
```


```{r}
trauma_cnty <- svyrdat %>%
  group_by(county) %>%
  summarize(se = std.error(trauma),
            trauma=mean(trauma, na.rm=T)) %>%
  mutate(lower=trauma-1.96*se,
         upper=trauma+1.96*se) %>%
  select(1,3:5) %>%
  arrange(desc(trauma))

trauma_cnty
```

```{r}
ggplot(trauma_cnty, aes(trauma, fct_reorder(county, trauma))) + 
  geom_vline(xintercept=trauma_mn[,1], size=1, alpha=.7, color="darkgoldenrod2") +
  #geom_vline(xintercept=4, size=1, alpha=.7, color="aquamarine3") + 
  geom_point(color="dodgerblue", size=3) + 
  geom_errorbar(aes(xmin=lower, xmax=upper),
                color="dodgerblue",
                width=0,
                size=1) +
  geom_label(aes(label=paste(round(trauma,3)*100, "%", sep="")), size=4, color="dodgerblue") +
  scale_x_continuous(limits=c(.4,1),
                     breaks=seq(.4,1, .1),
                     labels=percent_format(accuracy=1)) +
  labs(x="Incidence of any trauma",
       y="")

ggsave(here("output/viz/any trauma, by county label.png"),
       type="cairo",
       device="png",
       height=4,
       width=7)
```

<<<<<<< HEAD
=======
```{r}
trauma_cnty2 <- svyrdat %>%
  group_by(county) %>%
  summarize(se = std.error(trauma),
            trauma=survey_mean(trauma, na.rm=T)) %>%
  mutate(lower=trauma-1.96*se,
         upper=trauma+1.96*se) %>%
  select(1,3:5) %>%
  arrange(desc(trauma))

trauma_cnty2
```


>>>>>>> 53697d484cb70458c87d3338f2aaa536f3391614
# Factor analysis 

Using a composite variable for any sort of trauma is of uncertain utility. It may be more of interest to think of trauma as a psychosocial condition resulting from the stress of a household dealing with its schedule of shocks and stresses. We can conduct additional analysis to investigate whether the trauma variables cluster around specific types of trauma. 

### Three factor model

```{r}
fa.parallel(trauma,
            cor="tet")
```


```{r}
trauma_fa_3 <- fa(trauma,
                  nfactors=3,
                  cor="tet",
                  fm="ml",
                  scores="tenBerge")

trauma_fa_3
```

The first factor (ML1) is built on problems with personal relationships, behavior, and physical symptoms. 

The second factor (ML3) is built on problems with feelings and thoughts. 

The third factor (ML2) is built on problems with physical symptoms.

This three-factor model captures 87 percent of the variance across the six trauma variables. Correlation between factors is high. Model goodness of fit is high.  


```{r}
fa.diagram(trauma_fa_3)
```

For purposes of using a measure of psychosocial stress to help model household resilience, we might consider ML3 (problems with thoughts and feelings) to be the factor that best captures a generalized measure of mental or emotional stress. Problems with personal relationships and behavior (ML1) may capture behavioral issues unrelated to stress from the environment, while problems with physical symptoms (ML2) may capture sickness or injury that is unrelated to stress from the environment. In the three-factor model, the 'stress' factor accounts for 25 percent of the variance across the six trauma items. 

# Psychosocial stress

Alternatively, and for purposes of simplicity, we may also use the survey item for problems with feelings/emotions. 

```{r}
feelings_mn <- svyrdat %>%
  group_by() %>%
  summarize(trauma_feelings=survey_mean(trauma_feelings, na.rm=T))

feelings_mn
```

```{r}
feelings_cnty <- svyrdat %>%
  group_by(county) %>%
  summarize(se = std.error(trauma),
            trauma_feelings=mean(trauma_feelings, na.rm=T)) %>%
  mutate(lower=trauma_feelings-1.96*se,
         upper=trauma_feelings+1.96*se) %>%
  select(1,3:5) %>%
  arrange(desc(trauma_feelings))

feelings_cnty
<<<<<<< HEAD
```
=======

write_csv(feelings_cnty, here("output/tables/trauma feelings by county.csv"))

feelings_cnty_gt <- feelings_cnty %>%
  gt() %>%
  fmt_percent(2:4, decimals=1)

feelings_cnty_gt

gtsave(feelings_cnty_gt, here("output/tables/trauma feelings by county.rtf"))

```

>>>>>>> 53697d484cb70458c87d3338f2aaa536f3391614
```{r}
ggplot(feelings_cnty, aes(trauma_feelings, fct_reorder(county, trauma_feelings))) + 
  geom_vline(xintercept=feelings_mn[,1], size=1, alpha=.7, color="darkgoldenrod2") +
  #geom_vline(xintercept=4, size=1, alpha=.7, color="aquamarine3") + 
  geom_point(color="dodgerblue", size=3) + 
  geom_errorbar(aes(xmin=lower, xmax=upper),
                color="dodgerblue",
                width=0,
                size=1) +
  geom_label(aes(label=paste(round(trauma_feelings,3)*100, "%", sep="")), size=4, color="dodgerblue") +
  scale_x_continuous(limits=c(.22,1),
                     breaks=seq(.25,1, .1),
                     labels=percent_format(accuracy=1)) +
  labs(x="Incidence of psychosocial trauma",
       y="")

ggsave(here("output/viz/psychosocial trauma, by county label.png"),
       type="cairo",
       device="png",
       height=4,
       width=7)
```








